### 2017-02-10 paper.tex
initial

\documentclass{sig-alternate}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{array}
\usepackage{caption}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{verbatim}
\usepackage{colortbl}
\usepackage[table]{xcolor}

\definecolor{myGray}{gray}{0.8}

\newcommand\rankeq{\mathrel{\overset{\makebox[0pt]{\mbox{\normalfont\tiny\sffamily rank}}}{=}}}

\setlist[itemize]{noitemsep}  % remove space between list items

\begin{document}

\author{Garrick Sherman}

\title{Document Expansion with External Collections for Information Retrieval}

\maketitle
\begin{abstract}
\end{abstract}

\section{Introduction}\label{section.intro}

When using language models (LMs) to perform document retrieval, we treat the query and document texts as observations from unseen (and unobservable) probabilistic processes. In the query likelihood (QL) retrieval model, we rank each document by the likelihood that its language model would ``generate'' the query text. However, if the query is a sample from an underlying stochastic process, it is generally too sparse to fully represent an informtion need.

Relevance modeling is an extremely influential pseudo-relevance feedback technique that helps to allievate the problem of vocabulary mismatch. Instead of assuming that queries are observations sampled from \textit{document} models, we assume that both queries and documents are observations sampled from a \textit{relevance} model (RM) \cite{Lavrenko2001}. We can use this idea to expand the query representation into an estimate of the relevance model (see Section \ref{section.expanding.model.rm} for more details) and rank documents by the similarity of their estimated language model to the estimated RM.

As a form of pseudo-relevance feedback, part of the relevance modeling process involves assuming that top-ranked documents are relevant to the query. Although this assumption is not uniformly true, it is true of enough top-ranked documents that the estimated RM will be of good quality. That is, initially retrieved documents provide a good estimate of the underlying relevance model \textit{in their aggregate}; taken individually, documents are not assumed to accurately represent the underlying RM.

% We suggest that, given that a top-ranked document is, like a query, considered a limited observation of terms from a relevance model, documents may be expanded to better reflect their underlying relevance model. In this paper, we propose a method of document expansion that closely mirrors the process of relevance modeling. This document expansion process serves many of the same roles as traditional relevance modeling without excluding the use of RMs; indeed, our document expansion process is complementary to query expansion.

Relevance modeling makes use of a query likelihood weight, $P(Q|D)$, which helps to quantify the degree to which each document should contribute to the final RM. However, given that individual documents are not considered accurate representations of the relevance model $R$, we may reasonably be concerned that our estimate of $P(Q|D)$ is the result of chance. This concern applies to both high and low estimates of $P(Q|D)$, and, if true, we would expect this problem to affect the quality of our relevance models. We suggest that this may be solved by expanding documents: adding terms to a document should improve our estimates of the underlying language model and in turn improve the quality of retrieval results and relevance models based on these expanded documents.

In this paper, we propose a method of document expansion that closely mirrors the process of relevance modeling. This document expansion process serves many of the same roles as traditional relevance modeling without excluding the use of RMs; indeed, our document expansion process is complementary to query expansion. However, the concerns that lead us to expand documents in the first place---potentially inaccurate term probability estimates drawn from top-ranked documents---also apply to our document expansion procedure.

To help alleviate this, we introduce a general method of incorporating external document collections into the document expansion process. Our idea is that, while documents in individual collections may suffer from fairly high term frequency variance and other forms of bias, documents from multiple collections will likely average out to create good general purpose estimates. Specifically, we use Wikipedia as our external collection. We believe that, as a general encyclopedia, Wikipedia is most likely to provide unbiased language model estimates; that is, estimates of $P(Q|D)$ calculated where $D$ is from Wikipedia seem likely to exhibit minimal variance.

\section{Related Work}\label{section.related}

\subsection{Document Expansion in IR}\label{section.related.ir}

Document expansion has been well studied in information retrieval literature, e.g. \cite{Liu2004, Tao2006, Wei2006, Hubert2009, Singhal1999}. For example, Liu \& Croft propose a method of retrieval that uses document clusters to smooth document language models \cite{Liu2004}. Tao et al. propose a similar approach to that of Liu \& Croft, but with each document at the center of its own cluster; this helps to ensure that the expansion documents are as closely related to the target document as possible \cite{Tao2006}.

Our approach takes as its starting point that of Efron, Organisciak \& Fenlon \cite{Efron2012}, who issue very short microblog documents as pseudo-queries. They then expand the original document using these microblog documents retrieved for the pseudo-query. Their approach relates closely to that of relevance modeling \cite{Lavrenko2001}. We explore the application and adaptation of their work to different scenarios. First, Efron, Organisciak \& Fenlon are concerned with microblog retrieval, in which documents are extremely short---perhaps as small as a keyword query. In contrast, we are interested in performing document expansion with more typical full-length documents, such as those found in news and web corpora. Second, while their work used only the target document collection, we propose an expansion of their method that allows for multiple expansion corpora. Finally, we investigate pairing document expansion with query expansion.

\subsection{Incorporating External Collections}\label{section.external.collections}

The incorporation of external collections into document retrieval is a similarly common theme in the ad-hoc IR literature, particularly with respect to query expansion \cite{Diaz2006, Weerkamp2009, Li2007, Xu2009, Bendersky2012}. Of particular relevance to our work is that of Diaz \& Metzler, whose mixture of relevance models is the basis of our Eq. \ref{eq.ql-and-expansion-mult} \cite{Diaz2006}. Their model simply interpolates RMs built on different collections, weighting each by a query-independent quantity $P(c)$. Though based on this model, our approach is qualitatively different since Diaz \& Metzler were interested in query expansion, whereas we apply the technique to document expansion.

\section{Document Expansion Procedure}\label{section.expanding}

\subsection{Underlying Retrieval Model}\label{section.expanding.model}
Throughout this paper we rely on the language modeling retrieval framework \cite{Lafferty2001}, though this is not strictly necessary and imposes no particular mathematical constraints on our approach. More specifically, we employ the query likelihood (QL) and relevance modeling ranking methods.

\subsubsection{Query Likelihood}\label{section.expanding.model.ql}

Given a query $Q$ and a document $D$, we rank documents on $P(Q | \theta_D)$, where $\theta_D$ is the language model (typically a multinomial over the vocabulary $V$) that generated the text of document $D$.  Assuming independence among terms and a uniform distribution over documents, each document is scored by

\begin{flalign}\label{equation.ql}
\log P(Q | D) = \prod_{w \in Q} P(w | Q) \cdot \log P(w | \theta_D) .
\end{flalign}

\noindent We follow standard procedures for estimating the probabilities in Eq. \ref{equation.ql}.  We simply use the maximum likelihood estimate of $\hat{P}(w | Q) = \frac{c(w, Q)}{|Q|}$ where $c(w, Q)$ is the frequency of word $w$ in $Q$.  For $P(w | \theta_D)$ we estimate a smoothed language model by assuming that document language models
in a given collection have a Dirichlet prior distribution:

\begin{flalign}\label{equation.ql-dirichlet}
\hat{P}(w | \theta_D) = \frac{c(w, D) + \mu \hat{P}(w | C)}{|D| + \mu} 
\end{flalign}

\noindent where $\hat{P}(w | C)$ is the maximum likelihood estimate of the probability of seeing word $w$ in a ``background" collection $C$ (typically $C$ is the corpus from which $D$ is drawn), and $\mu \geq 0$ is the smoothing hyper-parameter.

\subsubsection{Relevance Modeling}\label{section.expanding.model.rm}

Relevance modeling is a form of pseudo-relevance feedback that uses top ranked documents to estimate a language model representing documents relevant to a query \cite{Lavrenko2001}. This language model, known as a relevance model, acts as a form of query expansion and is generally used with the KL divergence retrieval model \cite{Zhai2006} to score documents.

A relevance model takes the form of

\begin{flalign}\label{equation.rm1}
	P(w|R) = \sum_{D \in C} P(D) P(w|D) P(Q|D)
\end{flalign}

\noindent where $P(Q|D)$ is calculated as in Equation \ref{equation.ql} and essentially weights word $w$ in document $D$ by the query likelihood of the document. Though theoretically calculated over all words and documents, relevance models are more efficient and robust when calculated over only the top terms in only the top ranked documents. These parameters are referred to as $fbTerms$ and $fbDocs$ respectively in Table \ref{table.parameters}.

Because relevance models are prone to query drift, research has shown that linearly interpolating a relevance model with the original query model to improve performance:

\begin{flalign}\label{equation.rm3}
	P(w|Q') = (1-\alpha) P(w|R) + \alpha P(w|Q).
\end{flalign}

\noindent $\alpha$ is a mixing parameter controlling the influence of the original query. This form of relevance model is known as ``RM3'' and is the baseline used throughout this paper.

\subsection{Expanding with Document Pseudo-Queries}\label{section.expanding.queries}

To expand a document $D$, we begin by treating the text of $D$ as a pseudo-query which we pose against a collection of documents $C_E$.  To transform a document into a pseudo-query we apply two transformations.  First we remove all terms from $D$ that appear in the standard Indri stoplist\footnote{http://www.lemurproject.org/stopwords/stoplist.dft}.  Next, we prune our pseudo-query by retaining only the $0 < k \leq |D|$ most frequent words in the stopped text of $D$.  The integer variable $k$ is a parameter that we choose empirically.  Let $Q_D$ be the pseudo-query for $D$, consisting of the text of $D$ after our two transformations are applied.

We obtain a ranking of related documents, which we call expansion documents, by running $Q_D$ over an index $C_E$. More formally, we rank the documents in $C_E$ against $D$ using Eq. \ref{equation.ql}, substituting $Q_D$ for the query and $E_i$---the text of the $i^{th}$ expansion document---for the document. Let $\pi_i$ be the log-probability for expansion document $E_i$ with respect to $D$ given by Eq. \ref{equation.ql}.

We now have a ranked list of tuples $\{(E_1, \pi_1)$, $(E_2, \pi_2)$, $...$, $(E_N, \pi_N)\}$ relating expansion document $E_i$ to $D$ with log-probability $\pi_i$. We take the top $n$ documents where $0 \leq n \leq N$. We call these top documents $\mathcal{E}_D$ and designate them as our expansion documents for $D$.  Finally, we exponentiate each $\pi_i$ and normalize our retrieval scores so they sum to 1 over the $n$ retained documents.  Assuming a uniform prior over documents, we now have a probability distribution over our $n$ retained documents: $P(E | D)$.

Since this procedure does not depend on the query, we may compute $\mathcal{E}_D$ once at indexing time and reuse our expansion documents across queries.

\section{Document Expansion Retrieval Model}\label{section.model}

We would now like to incorporate our expansion documents into a retrieval model over documents. We assume that a query is generated by a mixture of the original document language model $\theta_D$ and a language model $\theta_E$ representing the expansion documents. We assume that $\theta_E$ can be estimated using the text of the expansion documents $\mathcal{E}_D$. This mixture model may be expressed as:
%
\begin{flalign}\label{eq.ql-and-expansion}
	\hat{P}^\lambda(Q|D) &= \prod_{i=1}^{|Q|} (1-\lambda) P(q_i|D) + \lambda P(q_i|\mathcal{E}_D)
\end{flalign}

\noindent with $0 \leq \lambda \leq 1$. The larger $\lambda$ is, the more we believe that the expansion documents are a good representation of $Q$ and the less we believe that the original document represents the ``true'' language model of $Q$. We estimate $P(q_i|\mathcal{E}_D)$ in expectation:
%
\begin{flalign}\label{eq.expansion-sum}
	P(q_i|\mathcal{E}_D) &= \sum_{E \in \mathcal{E}_D} P(q_i|E) P(E|D) .
\end{flalign}

\noindent Like $P(q_i|D)$, we estimate the probability of $q_i$ given expansion document $E$, $P(q_i|E)$, as a Dirichlet-smoothed query likelihood. By virtue of our expansion document scoring and normalization, we also have $P(E|D)$.

\subsection{Combining Evidence}\label{section.combining}

We investigate the use of multiple collections for document expansion. We expect a more diverse set of expansion documents to result in more robust (less biased) language models at the conclusion of the expansion process.

To expand a document $D$ given a set of collections $C = \{C_1, C_2, ..., C_n\}$, we first construct a set of expansion documents ${\mathcal{E}_D}_i$ using $C_i$ in the manner described in Section \ref{section.expanding}. We may incorporate these multiple sets of expansion documents by simply altering Eq. \ref{eq.ql-and-expansion} to sum over $\mathcal{E}_D$ terms:

\begin{flalign}\label{eq.ql-and-expansion-mult}
	\hat{P}^\lambda(Q|D) &= \prod_{i=1}^{|Q|} (1-\sum_{j=1}^n \lambda_{{\mathcal{E}_D}_j}) P(q_i|D) + \sum_{j=1}^n \lambda_{{\mathcal{E}_D}_j} P(q_i|{\mathcal{E}_D}_j)
\end{flalign}

\noindent where $0 \leq \sum_{j=1}^n \lambda_{{\mathcal{E}_D}_j} \leq 1$. As before, each value of $\lambda_{{\mathcal{E}_D}_j}$ reflects our confidence in that set of expansion documents accurately representing the query language model.

\subsection{Relevance Modeling with Expanded Documents}

While our approach serves much the same role as relevance modeling, the two techniques may in fact be used simultaneously. Practically, the relevance model may be computed on either the unexpanded or the expanded documents. However, there are two reasons why we would prefer the latter case: 
\begin{enumerate}
	\item Given our motivating intuition that document expansion allows for the more accurate estimation of document language models, we would expect that computing an RM using expanded documents should produce a more accurate relevance model.
	\item Part of the benefit of document expansion is that it may be performed at indexing time, so computing an RM on unexpanded documents ignores information that is already available.
\end{enumerate}

The addition of relevance modeling to our document expansion approach is therefore extremely straightforward: we simply compute the RM as in Eq. \ref{equation.rm1} substituting the expanded document for the original.

\section{Evaluation}\label{section.evaluation}

\subsection{Data}\label{section.evaluation.collections}

Although Eq. \ref{eq.ql-and-expansion-mult} allows for an arbitrary number of collections, for now we limit ourselves to two: the collection that the document appears in and Wikipedia. To this end, we make use of the September 1, 2015 dump of English Wikipedia. We build an Indri\footnote{http://www.lemurproject.org/indri/} index over the Wikipedia page text. The text of each page serves as the ``description text'' used in Eq. \ref{eq.expansion-sum}.

We test our approach using several TREC datasets:
\begin{itemize}
	\item The \textbf{AP} newswire collection from TREC disks 1 and 2 with topics 101-200.
	\item The \textbf{robust} 2004 topics, numbering 250, from TREC disks 4 and 5.
	\item The \textbf{wt10g} collection with the 100 topics from the 2000 and 2001 TREC Web tracks.
\end{itemize}

These datasets were chosen because they provide a good range of collection types, from relatively homogeneous with well-formed documents (AP) to heterogeneous with varied document quality (wt10g).

\subsection{Runs}\label{section.evaluation.runs}

For each collection, we produce eight runs representing a combination of expansion source and query expansion type.

\subsubsection{Expansion Source}\label{section.evaluation.runs.expansion}

We test each type of expansion source individually, with documents expanded using:
\begin{itemize}
	\item the target collection itself, called \textit{Self},
	\item Wikipedia, called \textit{Wiki}, or
	\item a mixture of the target collection and Wikipedia, called \textit{Double}.
\end{itemize}

We also include \textit{Baseline} runs that employ no query expansion. For each expansion source, we test both the query likelihood and RM3 variations to determine the effect of query expansion.

We remove stop words in documents and entity descriptions for all runs. For efficiency, we retrieve the top 1000 documents per query using the default Indri query likelihood implementation and re-rank these documents based on their expanded representations as described in Section \ref{section.model}.

\subsection{Parameters}\label{section.evaluation.parameters}

\begin{table}[htb]
\centering
\begin{tabular}{|c|p{0.29\textwidth}|c|} \hline
{\bf Param} & {\bf Meaning} & {\bf Value} \\ \hline
$k$ & The maximum number of document terms to use in constructing $Q_D$. & 20 \\ \hline
$n$ & The maximum number of expansion documents in $\mathcal{E}_D$. & 10 \\ \hline
$\lambda_{\mathcal{E}_D}$ & One of several related mixing parameters controlling the weights of $P(q|D)$ and $P(q|\mathcal{E}_D)$ & 0.0-1.0 \\ \hline
$\mu$ & Used for Dirichlet smoothing of both $P(q|D)$ and $P(q|E)$. & 2500 \\ \hline
$fbDocs$ & The number of feedback documents to use for RM3 runs. & 20 \\ \hline
$fbTerms$ & The number of terms per document to use for RM3 runs. & 20 \\ \hline
$\alpha$ & Mixing parameter controlling the weights of the original query and relevance model for RM3 runs. & 0.0-1.0 \\ \hline
\end{tabular}
\caption{Parameter settings for the document expansion procedure and retrieval model}
\label{table.parameters}
\end{table}

The various parameters required for our approach, along with their meanings and the values used in our experiments, are shown in Table \ref{table.parameters}.

%We sweep across values of $\lambda_{\mathcal{E}_D}$ and $n$ at intervals of 0.1 and 10 respectively to investigate the sensitivity of our model to these parameters. The results of these sweeps are shown in Figure \ref{figure.sweeps-ql} and discussed further in Section \ref{section.results}.

For this work, we set $k$ heuristically. In principle, this parameter need not be limited beyond the length of the document; however, this would increase computation time significantly, so we have opted to set it to the specified value. The parameter $n$ is similarly set heuristically to 10 expansion documents; see Section \ref{section.n-sensitivity} for a discussion of the performance sensitivity to the setting of $n$.

%To set the two $\lambda_{\mathcal{E}_D}$ values, we use 5-fold cross validation. This entails splitting each set of topics into five random groups (folds) and using four of them in concert with relevance judgments to determine optimal parameter settings, which we test using the fifth. By using each of the five folds as the test fold once, we produce results that fully cover the topic set; we combine these results in order to perform batch evaluation. Additionally, since the quality of the results depends in part on the initial random fold creation, we run the cross-validation repeatedly 75 times and report the average metric across these repeated runs. This helps ensure that strong performance is not the result of a beneficial but random division of documents.

To set the two $\lambda_{\mathcal{E}_D}$ values, we use 10-fold cross validation. This entails splitting each set of topics into ten random groups (folds) and using nine of them in concert with relevance judgments to determine optimal parameter settings, which we test using the tenth. By using each of the ten folds as the test fold once, we produce results that fully cover the topic set; we combine these results in order to perform batch evaluation.

\section{Results}\label{section.results}

\begin{table}[htbp]
\centering
\begin{tabular}{|c|l|l|l|l|} \hline
{\bf Collection} & {\bf Exp. Source} & {\bf Run} & {\bf MAP} & {\bf nDCG@20} \\ \hline\hline
\rule{0pt}{2.5ex} \multirow{8}{*}{AP} & \cellcolor{gray!50} & \cellcolor{gray!50}{\it QL} & \cellcolor{gray!50}0.2337 & \cellcolor{gray!50}0.4170 \\ \cline{3-5}
\rule{0pt}{2.5ex} & \cellcolor{gray!50} \multirow{-2}{*}{\it Baseline} & \cellcolor{gray!50}{\it RM3} & \cellcolor{gray!50}0.3310$^\uparrow$ & \cellcolor{gray!50}0.4855$^\uparrow$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Self} & {\it QL} & 0.2694$^\uparrow$ & 0.4519$^\uparrow$ \\ \cline{3-5}
\rule{0pt}{2.5ex} & & {\it RM3} & 0.3295$^{\uparrow *}$ & \textbf{0.4876}$^{\uparrow *}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Wiki} & {\it QL} & 0.2644$^\uparrow$ & 0.4582$^\uparrow$ \\ \cline{3-5}
\rule{0pt}{2.5ex} & & {\it  RM3} & 0.3334$^{\uparrow *}$ & 0.4811$^{\uparrow *}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Double} & {\it QL} & 0.2774$^{\uparrow SW}$ & 0.4734$^{\uparrow SW}$ \\ \cline{3-5}
\rule{0pt}{2.5ex} & & {\it RM3} & \textbf{0.3342}$^{\uparrow\Uparrow *S}$ & 0.4789$^\uparrow$ \\ \hline\hline
\rule{0pt}{2.5ex} \multirow{8}{*}{Robust} & \cellcolor{gray!50} & \cellcolor{gray!50}{\it QL} & \cellcolor{gray!50}0.2183 & \cellcolor{gray!50}0.3867 \\ \cline{3-5}
\rule{0pt}{2.5ex} & \cellcolor{gray!50} \multirow{-2}{*}{\it Baseline} & \cellcolor{gray!50}{\it RM3} & \cellcolor{gray!50}0.2639$^\uparrow$ & \cellcolor{gray!50}0.3908 \\ \cline{2-5}
\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Self} & {\it QL} & 0.2369$^\uparrow$ & 0.4036$^\uparrow$ \\ \cline{3-5}
\rule{0pt}{2.5ex} & & {\it RM3} & 0.2591$^{\uparrow\Downarrow *}$ & 0.3894$^{*}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Wiki} & {\it QL} & 0.2326$^\uparrow$ & 0.4040$^\uparrow$ \\ \cline{3-5}
\rule{0pt}{2.5ex} & & {\it RM3} & \textbf{0.2674}$^{\uparrow *}$ & 0.4201$^{\uparrow\Uparrow *}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Double} & {\it QL} & 0.2417$^{\uparrow W}$ & 0.4156$^{\uparrow\Uparrow SW}$ \\ \cline{3-5}
\rule{0pt}{2.5ex} & & {\it RM3} & 0.2672$^{\uparrow *S}$ & \textbf{0.4205}$^{\uparrow\Uparrow S}$ \\ \hline\hline
\rule{0pt}{2.5ex} \multirow{8}{*}{wt10g} & \cellcolor{gray!50} & \cellcolor{gray!50}{\it QL} & \cellcolor{gray!50}0.1683 & \cellcolor{gray!50}0.2816 \\ \cline{3-5}
\rule{0pt}{2.5ex} & \cellcolor{gray!50} \multirow{-2}{*}{\it Baseline} & \cellcolor{gray!50}{\it RM3} & \cellcolor{gray!50}0.1651 & \cellcolor{gray!50}0.2834 \\ \cline{2-5}
\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Self} & {\it QL} & 0.1660 & 0.2936 \\ \cline{3-5}
\rule{0pt}{2.5ex} & & {\it RM3} & 0.1694$^\Uparrow$ & 0.2758$^\Downarrow$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Wiki} & {\it QL} & 0.1780$^\uparrow$ & 0.3029$^\uparrow$ \\ \cline{3-5}
\rule{0pt}{2.5ex} & & {\it RM3} & \textbf{0.2089}$^{\uparrow\Uparrow *}$ & \textbf{0.3085}$^{\uparrow\Uparrow}$ \\ \cline{2-5}
\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Double} & {\it QL} & 0.1759$^{S}$ & 0.3148$^{\uparrow\Uparrow SW}$ \\ \cline{3-5}
\rule{0pt}{2.5ex} & & {\it RM3} & 0.2061$^{\uparrow\Uparrow *S}$ & 0.3082$^{\uparrow\Uparrow S}$ \\ \hline
\end{tabular}
\caption{Performance of runs using various expansion sources with (\textit{RM3}) and without (\textit{QL}) query expansion. Statistical significance at $\alpha = 0.05$ is marked with a variety of symbols: $\uparrow$ indicates improvement over the baseline QL run; $\Uparrow$ and $\Downarrow$ indicate improvement and decline respectively with respect to the baseline RM3 run; $^{*}$ indicates improvement over the QL run with the same expansion source; $^{S}$ and $^{W}$ indicate improvement over the \textit{self} and \textit{wiki} sources, respectively, of the same run type. Bolded runs are the highest raw score for an evaluation metric in a given collection, regardless of statistical significance.}
\label{table.performance}
\end{table}

Retrieval performance for various runs are shown in Table \ref{table.performance}. We use mean average precision (MAP) and normalized discounted cumulative gain at 20 (nDCG@20) to measure performance. Each metric has been optimized with 10-fold cross-validation.

The results confirm that document expansion provides benefit over a baseline query likelihood run---no run performs significantly worse than the baseline, and all expansion runs in AP and all but one expansion run in Robust improve over the baseline query likelihood run. % Note that baselines correspond to $\sum_{j=1}^n \lambda_{{\mathcal{E}_D}_j} = 0.0$.

Performance of RM3 runs is more surprising with improvement over the baseline RM3 occurring more rarely compared to improvement over the baseline QL. The data suggest that RM3 runs may be more effective in more heterogeneous collections: there are three RM3 improvements in Robust and six in wt10g, compared to only one in AP. This makes intuitive sense since a homogeneous collection would be expected to receive less benefit from query expansion. We can also see that an RM3 run typically improves over its QL counterpart, demonstrating that relevance modeling continues to operate effectively with the introduction of document expansion.

The effect of "double" runs---that is, runs expanded with both the target and external collection---was not as prominent as anticipated. In general, \textit{wiki} runs perform similarly to \textit{double} runs. However, the performance of \textit{double} runs \textit{is} visible when query expansion is ignored: five out of six \textit{double} QL runs show statistically significant improvement over \textit{wiki} QL runs. In one case (wt10g measuring nDCG@20) the \textit{double} QL run even outperforms the \textit{wiki} RM3 run with statistical significance.

\subsection{Sensitivity to $n$}\label{section.n-sensitivity}

\begin{figure*}[!htb]
\centering
\includegraphics[width=\columnwidth]{figures/n-sweep.pdf}
\caption{Sweeps over values of $n$, the number of entities, for each \textit{exp-ql} run.}
\label{figure.n-sweeps}
\end{figure*}

Similar to $k$, the value of $n$ may theoretically equal the number of expansion documents available, i.e. $|C_E|$; in practice, of course, this is infeasible, and $n$ will be substantially smaller. We must be careful in setting the value of $n$ for computational efficiency reasons: if $n$ is set high, we must process more documents. Figure \ref{figure.n-sweeps} shows sweeps over several values of $n$ for each target collection using our established 10-fold cross validation procedure with identical folds. Happily, the performance of our approach is not sensitive to the setting of $n$, and lower values generally perform as well or better than higher values. We therefore choose the value of 10 as an apparently safe value; this is a convenient result since it allows for more efficient document expansion.

\section{Conclusions}\label{section.conclusions}

The results indicate that our approach for expanding documents using Wikipedia and the document's original collection produces useful data for document retrieval purposes. Our simple document expansion model performs well compared to both a query likelihood and RM3 baseline.

In this paper, we have limited ourselves to using only two collections. However, future work may benefit from incorporating more collections to improve our language model estimates. Since our retrieval model performs \textit{document} expansion, we also plan to investigate its utility when paired with \textit{query} expansion techniques that employ knowledge base links.

\section{Acknowledgments}\label{section.acknowledgments}
This work was supported in part by the US National Science Foundation under Grant No. [blind]. Any opinions, findings, conclusions, or recommendations expressed are those of the authors and do not necessarily reflect the views of the National Science Foundation.

\bibliographystyle{abbrv}
\bibliography{library}

\end{document}

### 2017-02-14 paper.tex
updated draft

@@
 \usepackage{array}
+\usepackage{booktabs}
 \usepackage{caption}
@@
 \newcommand\rankeq{\mathrel{\overset{\makebox[0pt]{\mbox{\normalfont\tiny\sffamily rank}}}{=}}}
+\newcommand{\bigcell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}
 
@@
 
-\title{Document Expansion with External Collections for Information Retrieval}
+\title{Relevance Modeling with Documents Expanded Using External Collections}
 
@@
 \begin{abstract}
+Document expansion has been shown to improve the performance of information retrieval systems by augmenting documents' term probability estimates with those of similar documents, producing higher quality document representations.
+We propose a method to further improve document models by utilizing external collections as part of the document expansion process.
+Our approach is based on relevance modeling, a popular form of pseudo-relevance feedback; however, where relevance modeling is concerned with \textit{query} expansion, we are concerned with \textit{document} expansion.
+Our experiments demonstrate that the proposed model improves ad-hoc document retrieval performance on a variety of corpus types, with a particular benefit on more heterogeneous collections of documents.
 \end{abstract}
@@
 
-When using language models (LMs) to perform document retrieval, we treat the query and document texts as observations from unseen (and unobservable) probabilistic processes.
+%When using language models (LMs) to perform document retrieval, we treat the query and document texts as observations from unseen (and unobservable) probabilistic processes.
 In the query likelihood (QL) retrieval model, we rank each document by the likelihood that its language model would ``generate'' the query text.
@@
 
-Relevance modeling is an extremely influential pseudo-relevance feedback technique that helps to allievate the problem of vocabulary mismatch.
-Instead of assuming that queries are observations sampled from \textit{document} models, we assume that both queries and documents are observations sampled from a \textit{relevance} model (RM) \cite{Lavrenko2001}.
-We can use this idea to expand the query representation into an estimate of the relevance model (see Section \ref{section.expanding.model.rm} for more details) and rank documents by the similarity of their estimated language model to the estimated RM.
+Relevance modeling is an extremely influential pseudo-relevance feedback technique based on language modeling in which we assume that both queries and documents are observations sampled from a \textit{relevance} model (RM) \cite{Lavrenko2001}, which is a probability distribution over terms in relevant documents.
+Because we do not have true relevance feedback, relevance modeling makes use of the query likelihood, $P(Q|D)$, to quantify the degree to which each document should contribute to the final model $R$.
+However, since no document is perfectly representative of its underlying generative model, we may be reasonably concerned that our estimate of $P(Q|D)$ is the result of chance.
+That is, there is no guarantee that $D$ is a representative sample from $R$.
+The quality of our RM, therefore, may benefit from a higher quality document representation than that which is available in the collection.
 
-As a form of pseudo-relevance feedback, part of the relevance modeling process involves assuming that top-ranked documents are relevant to the query.
-Although this assumption is not uniformly true, it is true of enough top-ranked documents that the estimated RM will be of good quality.
-That is, initially retrieved documents provide a good estimate of the underlying relevance model \textit{in their aggregate}; taken individually, documents are not assumed to accurately represent the underlying RM.
+We employ two techniques to attempt to improve our document language models: document expansion and the use of external document collections.
+Expandeded documents are expected to exhibit less random variation in term frequencies, improving probability estimates.
+We hope that estimates may be further refined by expanding documents using \textit{external} collections, thereby avoiding any term bias that relevant documents in an individual collection may exhibit.
 
-% We suggest that, given that a top-ranked document is, like a query, considered a limited observation of terms from a relevance model, documents may be expanded to better reflect their underlying relevance model.
-In this paper, we propose a method of document expansion that closely mirrors the process of relevance modeling.
-This document expansion process serves many of the same roles as traditional relevance modeling without excluding the use of RMs; indeed, our document expansion process is complementary to query expansion.
-
-Relevance modeling makes use of a query likelihood weight, $P(Q|D)$, which helps to quantify the degree to which each document should contribute to the final RM.
-However, given that individual documents are not considered accurate representations of the relevance model $R$, we may reasonably be concerned that our estimate of $P(Q|D)$ is the result of chance.
-This concern applies to both high and low estimates of $P(Q|D)$, and, if true, we would expect this problem to affect the quality of our relevance models.
+%This concern applies to both high and low estimates of $P(Q|D)$, and, if true, we would expect this problem to affect the quality of our relevance models.
 We suggest that this may be solved by expanding documents: adding terms to a document should improve our estimates of the underlying language model and in turn improve the quality of retrieval results and relevance models based on these expanded documents.
 
-In this paper, we propose a method of document expansion that closely mirrors the process of relevance modeling.
-This document expansion process serves many of the same roles as traditional relevance modeling without excluding the use of RMs; indeed, our document expansion process is complementary to query expansion.
-However, the concerns that lead us to expand documents in the first place---potentially inaccurate term probability estimates drawn from top-ranked documents---also apply to our document expansion procedure.
+%We can use this idea to expand the query representation into an estimate of the relevance model (see Section \ref{section.expanding.model.rm} for more details) and rank documents by the similarity of their estimated language model to the estimated RM.
 
-To help alleviate this, we introduce a general method of incorporating external document collections into the document expansion process.
-Our idea is that, while documents in individual collections may suffer from fairly high term frequency variance and other forms of bias, documents from multiple collections will likely average out to create good general purpose estimates.
-Specifically, we use Wikipedia as our external collection.
-We believe that, as a general encyclopedia, Wikipedia is most likely to provide unbiased language model estimates; that is, estimates of $P(Q|D)$ calculated where $D$ is from Wikipedia seem likely to exhibit minimal variance.
+Our study differs from prior work in a few important ways.
+Previous investigations into document expansion have tended to use only the target collection to expand documents, while our work explores the use of one or more distinct collections.
+In contrast, most existing work involving external corpora in ad-hoc information retrieval has focused on \textit{query} expansion; we are interested in incorporating external collections for purposes of \textit{document} expansion.
 
@@
 Our approach takes as its starting point that of Efron, Organisciak \& Fenlon \cite{Efron2012}, who issue very short microblog documents as pseudo-queries.
-They then expand the original document using these microblog documents retrieved for the pseudo-query.
-Their approach relates closely to that of relevance modeling \cite{Lavrenko2001}.
+They then expand the original document using those microblog documents retrieved for the pseudo-query in a manner closely related to relevance modeling \cite{Lavrenko2001}.
 We explore the application and adaptation of their work to different scenarios.
@@
 In contrast, we are interested in performing document expansion with more typical full-length documents, such as those found in news and web corpora.
-Second, while their work used only the target document collection, we propose an expansion of their method that allows for multiple expansion corpora.
+Second, while their work used only the target document collection, we propose an extension of their method that allows for multiple expansion corpora.
 Finally, we investigate pairing document expansion with query expansion.
@@
 \subsection{Underlying Retrieval Model}\label{section.expanding.model}
-Throughout this paper we rely on the language modeling retrieval framework \cite{Lafferty2001}, though this is not strictly necessary and imposes no particular mathematical constraints on our approach.
-More specifically, we employ the query likelihood (QL) and relevance modeling ranking methods.
+Throughout this paper we rely on the language modeling retrieval framework \cite{Lafferty2001}. More specifically, we employ the query likelihood (QL) and relevance modeling ranking methods.
 
@@
 
-\noindent $\alpha$ is a mixing parameter controlling the influence of the original query. This form of relevance model is known as ``RM3'' and is the baseline used throughout this paper.
+\noindent $\alpha$ is a mixing parameter controlling the influence of the original query. This form of relevance model is known as ``RM3.''
 
@@
 
+\subsection{Basic Model}\label{section.model.basic}
+
 We would now like to incorporate our expansion documents into a retrieval model over documents.
@@
 We investigate the use of multiple collections for document expansion.
-We expect a more diverse set of expansion documents to result in more robust (less biased) language models at the conclusion of the expansion process.
+We expect a more diverse set of expansion documents to result in more robust language models at the conclusion of the expansion process.
 
@@
 
-While our approach serves much the same role as relevance modeling, the two techniques may in fact be used simultaneously.
-Practically, the relevance model may be computed on either the unexpanded or the expanded documents.
-However, there are two reasons why we would prefer the latter case:
-\begin{enumerate}
-	\item Given our motivating intuition that document expansion allows for the more accurate estimation of document language models, we would expect that computing an RM using expanded documents should produce a more accurate relevance model.
-	\item Part of the benefit of document expansion is that it may be performed at indexing time, so computing an RM on unexpanded documents ignores information that is already available.
-\end{enumerate}
+Our model is complementary to that of relevance modeling.
+Given our motivating intuition that document expansion allows for the more accurate estimation of document language models, we would expect that computing an RM using expanded documents should produce a more accurate relevance model.
+Further, since document expansion may be performed at indexing time, computing an RM on expanded documents is no less efficient than doing so on unexpanded documents.
 
@@
 Although Eq.
-\ref{eq.ql-and-expansion-mult} allows for an arbitrary number of collections, for now we limit ourselves to two: the collection that the document appears in and Wikipedia.
-To this end, we make use of the September 1, 2015 dump of English Wikipedia.
+\ref{eq.ql-and-expansion-mult} allows for an arbitrary number of collections, for now we limit ourselves to two: the collection that the document appears in (the ``target'' collection) and Wikipedia; the latter, as a general knowledge encyclopedia, is hypothesized to yield relatively unbiased probability estimates.
 We build an Indri\footnote{http://www.lemurproject.org/indri/} index over the Wikipedia page text.
-The text of each page serves as the ``description text'' used in Eq.
-\ref{eq.expansion-sum}.
 
@@
 	\item Wikipedia, called \textit{Wiki}, or
-	\item a mixture of the target collection and Wikipedia, called \textit{Double}.
+	\item a mixture of the previous two, called \textit{Double}.
+	\item no expansion, called \textit{Baseline}
 \end{itemize}
 
-We also include \textit{Baseline} runs that employ no query expansion. For each expansion source, we test both the query likelihood and RM3 variations to determine the effect of query expansion.
+For each expansion source, both the QL and RM3 variations are tested.
 
-We remove stop words in documents and entity descriptions for all runs.
+Stop words are removed from the query and document pseudo-query for all runs.
 For efficiency, we retrieve the top 1000 documents per query using the default Indri query likelihood implementation and re-rank these documents based on their expanded representations as described in Section \ref{section.model}.
@@
 
-%We sweep across values of $\lambda_{\mathcal{E}_D}$ and $n$ at intervals of 0.1 and 10 respectively to investigate the sensitivity of our model to these parameters.
-The results of these sweeps are shown in Figure \ref{figure.sweeps-ql} and discussed further in Section \ref{section.results}.
-
 For this work, we set $k$ heuristically.
-In principle, this parameter need not be limited beyond the length of the document; however, this would increase computation time significantly, so we have opted to set it to the specified value.
+In principle, this parameter need not be limited beyond the length of the document; however, this would increase computation time significantly, so we have opted to set it to a reasonable value.
 The parameter $n$ is similarly set heuristically to 10 expansion documents; see Section \ref{section.n-sensitivity} for a discussion of the performance sensitivity to the setting of $n$.
 
-%To set the two $\lambda_{\mathcal{E}_D}$ values, we use 5-fold cross validation.
-This entails splitting each set of topics into five random groups (folds) and using four of them in concert with relevance judgments to determine optimal parameter settings, which we test using the fifth.
-By using each of the five folds as the test fold once, we produce results that fully cover the topic set; we combine these results in order to perform batch evaluation.
-Additionally, since the quality of the results depends in part on the initial random fold creation, we run the cross-validation repeatedly 75 times and report the average metric across these repeated runs.
-This helps ensure that strong performance is not the result of a beneficial but random division of documents.
-
-To set the two $\lambda_{\mathcal{E}_D}$ values, we use 10-fold cross validation.
-This entails splitting each set of topics into ten random groups (folds) and using nine of them in concert with relevance judgments to determine optimal parameter settings, which we test using the tenth.
-By using each of the ten folds as the test fold once, we produce results that fully cover the topic set; we combine these results in order to perform batch evaluation.
+The values of $\lambda_{\mathcal{E}_D}$ and $\alpha$, are determined using 10-fold cross-validation.
+In the training stage, we sweep over parameter values in intervals of 0.1.
+The results of each test fold for a given run are concatenated to form a complete set of topics.
 
@@
 
-\begin{table}[htbp]
+\begin{figure*}
 \centering
-\begin{tabular}{|c|l|l|l|l|} \hline
-{\bf Collection} & {\bf Exp. Source} & {\bf Run} & {\bf MAP} & {\bf nDCG@20} \\ \hline\hline
+\includegraphics[width=\linewidth]{figures/expansion-sweep.pdf}
+\caption{Sweeps over values of $n$, the number of expansion documents.}
+\label{figure.n-sweeps}
+\end{figure*}
+
+\begin{table}
+\begin{tabular}{|c|c|c|l|l|} \hline
+{\bf Corpus} & {\bf \bigcell{l}{Exp. \\ Source}} & {\bf Run} & {\bf MAP} & {\bf nDCG@20} \\ \hline\hline
 \rule{0pt}{2.5ex} \multirow{8}{*}{AP} & \cellcolor{gray!50} & \cellcolor{gray!50}{\it QL} & \cellcolor{gray!50}0.2337 & \cellcolor{gray!50}0.4170 \\ \cline{3-5}
@@
 \caption{Performance of runs using various expansion sources with (\textit{RM3}) and without (\textit{QL}) query expansion.
-Statistical significance at $\alpha = 0.05$ is marked with a variety of symbols: $\uparrow$ indicates improvement over the baseline QL run; $\Uparrow$ and $\Downarrow$ indicate improvement and decline respectively with respect to the baseline RM3 run; $^{*}$ indicates improvement over the QL run with the same expansion source; $^{S}$ and $^{W}$ indicate improvement over the \textit{self} and \textit{wiki} sources, respectively, of the same run type.
-Bolded runs are the highest raw score for an evaluation metric in a given collection, regardless of statistical significance.}
+Statistical significance at $p \leq 0.05$ is marked with a variety of symbols: $\uparrow$ indicates improvement over the baseline QL run; $\Uparrow$ and $\Downarrow$ indicate improvement and decline respectively with respect to the baseline RM3 run; $^{*}$ indicates improvement over the QL run with the same expansion source; $^{S}$ and $^{W}$ indicate improvement over the \textit{self} and \textit{wiki} sources, respectively, of the same run type.
+Bolded runs are the highest raw score for an evaluation metric in a given collection.}
 \label{table.performance}
@@
 
-The results confirm that document expansion provides benefit over a baseline query likelihood run---no run performs significantly worse than the baseline, and all expansion runs in AP and all but one expansion run in Robust improve over the baseline query likelihood run.
+The results confirm that document expansion provides benefit over a baseline query likelihood run---no run performs significantly worse than the baseline, and most runs improve over the baseline query likelihood run.
 % Note that baselines correspond to $\sum_{j=1}^n \lambda_{{\mathcal{E}_D}_j} = 0.0$.
@@
 
-The effect of "double" runs---that is, runs expanded with both the target and external collection---was not as prominent as anticipated.
 In general, \textit{wiki} runs perform similarly to \textit{double} runs.
-However, the performance of \textit{double} runs \textit{is} visible when query expansion is ignored: five out of six \textit{double} QL runs show statistically significant improvement over \textit{wiki} QL runs.
+However, the strong performance of \textit{double} runs \textit{is} visible when query expansion is ignored: five out of six \textit{double} QL runs show statistically significant improvement over \textit{wiki} QL runs.
 In one case (wt10g measuring nDCG@20) the \textit{double} QL run even outperforms the \textit{wiki} RM3 run with statistical significance.
 
-\subsection{Sensitivity to $n$}\label{section.n-sensitivity}
+\subsection{Sensitivity to \boldmath$n$}\label{section.n-sensitivity}
 
-\begin{figure*}[!htb]
-\centering
-\includegraphics[width=\columnwidth]{figures/n-sweep.pdf}
-\caption{Sweeps over values of $n$, the number of entities, for each \textit{exp-ql} run.}
-\label{figure.n-sweeps}
-\end{figure*}
-
-Similar to $k$, the value of $n$ may theoretically equal the number of expansion documents available, i.e.
-$|C_E|$; in practice, of course, this is infeasible, and $n$ will be substantially smaller.
-We must be careful in setting the value of $n$ for computational efficiency reasons: if $n$ is set high, we must process more documents.
-Figure \ref{figure.n-sweeps} shows sweeps over several values of $n$ for each target collection using our established 10-fold cross validation procedure with identical folds.
-Happily, the performance of our approach is not sensitive to the setting of $n$, and lower values generally perform as well or better than higher values.
+Figure \ref{figure.n-sweeps} shows sweeps over several values of $n$, the number of expansion documents, for each target collection using our established 10-fold cross-validation procedure with identical folds.
+The sensitivity to $n$ is not pronounced at $n \geq 5$, and what little variation exists is not consistent across collections.
 We therefore choose the value of 10 as an apparently safe value; this is a convenient result since it allows for more efficient document expansion.
@@
 Our simple document expansion model performs well compared to both a query likelihood and RM3 baseline.
-
-In this paper, we have limited ourselves to using only two collections.
-However, future work may benefit from incorporating more collections to improve our language model estimates.
-Since our retrieval model performs \textit{document} expansion, we also plan to investigate its utility when paired with \textit{query} expansion techniques that employ knowledge base links.
 

### 2017-02-14 paper.tex
only one model section to save space, and other small changes

@@
 
-\subsection{Basic Model}\label{section.model.basic}
-
 We would now like to incorporate our expansion documents into a retrieval model over documents.
-We assume that a query is generated by a mixture of the original document language model $\theta_D$ and a language model $\theta_E$ representing the expansion documents.
-We assume that $\theta_E$ can be estimated using the text of the expansion documents $\mathcal{E}_D$.
+We assume that a query is generated by a mixture of the original document language model $\theta_D$ and language models ${\theta_E}_j$ representing the expansion documents each corpus $C_j \in \{C_1, C_2, ..., C_n\}$.
+We assume that ${\theta_E}_j$ can be estimated using the text of the expansion documents ${\mathcal{E}_D}_j$ in corpus $C_j$.
 This mixture model may be expressed as:
 %
-\begin{flalign}\label{eq.ql-and-expansion}
-	\hat{P}^\lambda(Q|D) &= \prod_{i=1}^{|Q|} (1-\lambda) P(q_i|D) + \lambda P(q_i|\mathcal{E}_D)
+\begin{flalign}\label{eq.ql-and-expansion-mult}
+	\hat{P}^\lambda(Q|D) &= \prod_{i=1}^{|Q|} (1-\sum_{j=1}^n \lambda_{{\mathcal{E}_D}_j}) P(q_i|D) + \sum_{j=1}^n \lambda_{{\mathcal{E}_D}_j} P(q_i|{\mathcal{E}_D}_j)
 \end{flalign}
+%\begin{flalign}\label{eq.ql-and-expansion}
+%	\hat{P}^\lambda(Q|D) &= \prod_{i=1}^{|Q|} (1-\lambda) P(q_i|D) + \lambda P(q_i|\mathcal{E}_D)
+%\end{flalign}
 
-\noindent with $0 \leq \lambda \leq 1$.
-The larger $\lambda$ is, the more we believe that the expansion documents are a good representation of $Q$ and the less we believe that the original document represents the ``true'' language model of $Q$.
-We estimate $P(q_i|\mathcal{E}_D)$ in expectation:
-%
+\noindent where $0 \leq \sum_{j=1}^n \lambda_{{\mathcal{E}_D}_j} \leq 1$. We estimate $P(q_i|{\mathcal{E}_D}_j)$ in expectation:
+% %The larger $\lambda$ is, the more we believe that the expansion documents are a good representation of $Q$ and the less we believe that the original document represents the ``true'' language model of $Q$.
 \begin{flalign}\label{eq.expansion-sum}
-	P(q_i|\mathcal{E}_D) &= \sum_{E \in \mathcal{E}_D} P(q_i|E) P(E|D) .
+	P(q_i|{\mathcal{E}_D}_j) &= \sum_{E \in {\mathcal{E}_D}_j} P(q_i|E) P(E|D) .
 \end{flalign}
@@
 By virtue of our expansion document scoring and normalization, we also have $P(E|D)$.
-
-\subsection{Combining Evidence}\label{section.combining}
-
-We investigate the use of multiple collections for document expansion.
-We expect a more diverse set of expansion documents to result in more robust language models at the conclusion of the expansion process.
-
-To expand a document $D$ given a set of collections $C = \{C_1, C_2, ..., C_n\}$, we first construct a set of expansion documents ${\mathcal{E}_D}_i$ using $C_i$ in the manner described in Section \ref{section.expanding}.
-We may incorporate these multiple sets of expansion documents by simply altering Eq.
-\ref{eq.ql-and-expansion} to sum over $\mathcal{E}_D$ terms:
-
-\begin{flalign}\label{eq.ql-and-expansion-mult}
-	\hat{P}^\lambda(Q|D) &= \prod_{i=1}^{|Q|} (1-\sum_{j=1}^n \lambda_{{\mathcal{E}_D}_j}) P(q_i|D) + \sum_{j=1}^n \lambda_{{\mathcal{E}_D}_j} P(q_i|{\mathcal{E}_D}_j)
-\end{flalign}
-
-\noindent where $0 \leq \sum_{j=1}^n \lambda_{{\mathcal{E}_D}_j} \leq 1$.
-As before, each value of $\lambda_{{\mathcal{E}_D}_j}$ reflects our confidence in that set of expansion documents accurately representing the query language model.
+This general model may be used with any number of expansion corpora.
 
@@
 Although Eq.
-\ref{eq.ql-and-expansion-mult} allows for an arbitrary number of collections, for now we limit ourselves to two: the collection that the document appears in (the ``target'' collection) and Wikipedia; the latter, as a general knowledge encyclopedia, is hypothesized to yield relatively unbiased probability estimates.
+\ref{eq.ql-and-expansion-mult} allows for an arbitrary number of collections, for now we limit ourselves to two: the collection that the document appears in (the ``target'' collection) and Wikipedia\footnote{http://en.wikipedia.org}; the latter, as a general knowledge encyclopedia, is hypothesized to yield relatively unbiased probability estimates.
 We build an Indri\footnote{http://www.lemurproject.org/indri/} index over the Wikipedia page text.
@@
 
-These datasets were chosen because they provide a good range of collection types, from relatively homogeneous with well-formed documents (AP) to heterogeneous with varied document quality (wt10g).
+These datasets provide a good range of collection types, from relatively homogeneous with well-formed documents (AP) to heterogeneous with varied document quality (wt10g).
 
@@
 
-Stop words are removed from the query and document pseudo-query for all runs.
+Stop words are removed from the query.
 For efficiency, we retrieve the top 1000 documents per query using the default Indri query likelihood implementation and re-rank these documents based on their expanded representations as described in Section \ref{section.model}.
@@
 For this work, we set $k$ heuristically.
-In principle, this parameter need not be limited beyond the length of the document; however, this would increase computation time significantly, so we have opted to set it to a reasonable value.
-The parameter $n$ is similarly set heuristically to 10 expansion documents; see Section \ref{section.n-sensitivity} for a discussion of the performance sensitivity to the setting of $n$.
+In principle, this parameter need not be limited beyond the length of the document; however, this would increase computation time significantly, so we have set it to a reasonable value.
+The parameter $n$ is also set heuristically; see Section \ref{section.n-sensitivity} for a discussion of the performance sensitivity to the setting of $n$.
 
@@
 In the training stage, we sweep over parameter values in intervals of 0.1.
-The results of each test fold for a given run are concatenated to form a complete set of topics.
+The concatenated results of each test fold form a complete set of topics.
 

### 2017-02-14 paper.tex
several small updates; conclusion rewritten

@@
 
-Relevance modeling is an extremely influential pseudo-relevance feedback technique based on language modeling in which we assume that both queries and documents are observations sampled from a \textit{relevance} model (RM) \cite{Lavrenko2001}, which is a probability distribution over terms in relevant documents.
-Because we do not have true relevance feedback, relevance modeling makes use of the query likelihood, $P(Q|D)$, to quantify the degree to which each document should contribute to the final model $R$.
+Relevance modeling is an extremely influential pseudo-relevance feedback technique in which we assume that both queries and documents are observations sampled from a relevance model (RM) \cite{Lavrenko2001}, which is a probability distribution over terms in relevant documents.
+Because we do not have true relevance feedback, relevance modeling makes use of the query likelihood, $P(Q|D)$, to quantify the degree to which words in each document should contribute to the final model $R$.
 However, since no document is perfectly representative of its underlying generative model, we may be reasonably concerned that our estimate of $P(Q|D)$ is the result of chance.
@@
 Expandeded documents are expected to exhibit less random variation in term frequencies, improving probability estimates.
-We hope that estimates may be further refined by expanding documents using \textit{external} collections, thereby avoiding any term bias that relevant documents in an individual collection may exhibit.
+We hope that estimates may be further refined by expanding documents using \textit{external} collections, thereby avoiding any term bias exhibited by relevant documents in an individual collection.
 
@@
 Previous investigations into document expansion have tended to use only the target collection to expand documents, while our work explores the use of one or more distinct collections.
-In contrast, most existing work involving external corpora in ad-hoc information retrieval has focused on \textit{query} expansion; we are interested in incorporating external collections for purposes of \textit{document} expansion.
+Conversely, most existing work involving external corpora in ad-hoc information retrieval has focused on \textit{query} expansion; we are interested in incorporating external collections for purposes of \textit{document} expansion.
 
@@
 Document expansion has been well studied in information retrieval literature, e.g.
-\cite{Liu2004, Tao2006, Wei2006, Hubert2009, Singhal1999}.
+\cite{Liu2004, Singhal1999, Tao2006, Wei2006}.
 For example, Liu \& Croft propose a method of retrieval that uses document clusters to smooth document language models \cite{Liu2004}.
 Tao et al.
-propose a similar approach to that of Liu \& Croft, but with each document at the center of its own cluster; this helps to ensure that the expansion documents are as closely related to the target document as possible \cite{Tao2006}.
+propose a similar approach but place each document at the center of its own cluster; this helps to ensure that the expansion documents are as closely related to the target document as possible \cite{Tao2006}.
 
 Our approach takes as its starting point that of Efron, Organisciak \& Fenlon \cite{Efron2012}, who issue very short microblog documents as pseudo-queries.
-They then expand the original document using those microblog documents retrieved for the pseudo-query in a manner closely related to relevance modeling \cite{Lavrenko2001}.
+They employ a procedure closely related to relevance modeling \cite{Lavrenko2001} to expand the original document using those microblog documents retrieved for the pseudo-query.
 We explore the application and adaptation of their work to different scenarios.
@@
 Second, while their work used only the target document collection, we propose an extension of their method that allows for multiple expansion corpora.
-Finally, we investigate pairing document expansion with query expansion.
+Finally, we investigate pairing document expansion with query expansion, which their work suggests may be problematic in the microblog domain.
 
@@
 
-The incorporation of external collections into document retrieval is a similarly common theme in the ad-hoc IR literature, particularly with respect to query expansion \cite{Diaz2006, Weerkamp2009, Li2007, Xu2009, Bendersky2012}.
+The incorporation of external collections into document retrieval is a similarly common theme in the ad-hoc IR literature, particularly with respect to query expansion \cite{Bendersky2012, Diaz2006, Li2007, Weerkamp2009, Xu2009}.
 Of particular relevance to our work is that of Diaz \& Metzler, whose mixture of relevance models is the basis of our Eq.
@@
 Their model simply interpolates RMs built on different collections, weighting each by a query-independent quantity $P(c)$.
-Though based on this model, our approach is qualitatively different since Diaz \& Metzler were interested in query expansion, whereas we apply the technique to document expansion.
+Though our work bears similarities, Diaz \& Metzler are interested in query expansion, whereas we apply the technique as one piece in a document expansion model.
 
@@
 \subsection{Underlying Retrieval Model}\label{section.expanding.model}
-Throughout this paper we rely on the language modeling retrieval framework \cite{Lafferty2001}. More specifically, we employ the query likelihood (QL) and relevance modeling ranking methods.
+Throughout this paper we rely on the language modeling retrieval framework \cite{Lafferty2001}. More specifically, we employ query likelihood (QL) and relevance modeling for ranking.
 
@@
 Relevance modeling is a form of pseudo-relevance feedback that uses top ranked documents to estimate a language model representing documents relevant to a query \cite{Lavrenko2001}.
-This language model, known as a relevance model, acts as a form of query expansion and is generally used with the KL divergence retrieval model \cite{Zhai2006} to score documents.
+%This language model, known as a relevance model, acts as a form of query expansion and is generally used with the KL divergence retrieval model \cite{Zhai2006} to score documents.
 
@@
 
-\noindent where $P(Q|D)$ is calculated as in Equation \ref{equation.ql} and essentially weights word $w$ in document $D$ by the query likelihood of the document.
-Though theoretically calculated over all words and documents, relevance models are more efficient and robust when calculated over only the top terms in only the top ranked documents.
+\noindent where $P(Q|D)$ is calculated as in Eq.
+\ref{equation.ql} and essentially weights word $w$ in $D$ by the query likelihood of the document.
+Relevance models are most efficient and robust when calculated over only the top terms in only the top ranked documents.
 These parameters are referred to as $fbTerms$ and $fbDocs$ respectively in Table \ref{table.parameters}.
 
-Because relevance models are prone to query drift, research has shown that linearly interpolating a relevance model with the original query model to improve performance:
+Because relevance models are prone to query drift, it is often desirable to linearly interpolate an RM with the original query model to improve performance:
 
@@
 We would now like to incorporate our expansion documents into a retrieval model over documents.
-We assume that a query is generated by a mixture of the original document language model $\theta_D$ and language models ${\theta_E}_j$ representing the expansion documents each corpus $C_j \in \{C_1, C_2, ..., C_n\}$.
+We assume that a query is generated by a mixture of the original document language model $\theta_D$ and language models ${\theta_E}_j$ representing the expansion documents in each corpus $C_j \in \{C_1, C_2, ..., C_n\}$.
 We assume that ${\theta_E}_j$ can be estimated using the text of the expansion documents ${\mathcal{E}_D}_j$ in corpus $C_j$.
@@
 
-Our model is complementary to that of relevance modeling.
-Given our motivating intuition that document expansion allows for the more accurate estimation of document language models, we would expect that computing an RM using expanded documents should produce a more accurate relevance model.
-Further, since document expansion may be performed at indexing time, computing an RM on expanded documents is no less efficient than doing so on unexpanded documents.
-
-The addition of relevance modeling to our document expansion approach is therefore extremely straightforward: we simply compute the RM as in Eq.
-\ref{equation.rm1} substituting the expanded document for the original.
+Given our motivating intuition that document expansion allows for the more accurate estimation of document language models, we would expect that an RM computed using expanded documents should be more accurate than a standard RM.
+We therefore compute an RM3 as in Eqs.
+\ref{equation.rm1} and \ref{equation.rm3}, substituting the expanded document for the original.
 
@@
 Although Eq.
-\ref{eq.ql-and-expansion-mult} allows for an arbitrary number of collections, for now we limit ourselves to two: the collection that the document appears in (the ``target'' collection) and Wikipedia\footnote{http://en.wikipedia.org}; the latter, as a general knowledge encyclopedia, is hypothesized to yield relatively unbiased probability estimates.
+\ref{eq.ql-and-expansion-mult} allows for an arbitrary number of collections, for now we limit ourselves to two: the collection that the document appears in (the ``target'' collection) and Wikipedia\footnote{http://en.wikipedia.org}.
+The latter, as a general encyclopedia, is hypothesized to yield relatively unbiased probability estimates.
 We build an Indri\footnote{http://www.lemurproject.org/indri/} index over the Wikipedia page text.
 
-We test our approach using several TREC datasets:
+We test our approach using TREC datasets:
 \begin{itemize}
@@
 \begin{itemize}
-	\item the target collection itself, called \textit{Self},
-	\item Wikipedia, called \textit{Wiki}, or
-	\item a mixture of the previous two, called \textit{Double}.
-	\item no expansion, called \textit{Baseline}
+	\item no expansion, called \textit{baseline};
+	\item the target collection itself, called \textit{self};
+	\item Wikipedia, called \textit{wiki}; or
+	\item a mixture of the previous two, called \textit{double}.
 \end{itemize}
 
-For each expansion source, both the QL and RM3 variations are tested.
+\noindent For each source, both the QL and RM3 variations are tested.
 
 Stop words are removed from the query.
-For efficiency, we retrieve the top 1000 documents per query using the default Indri query likelihood implementation and re-rank these documents based on their expanded representations as described in Section \ref{section.model}.
+For efficiency, we retrieve the top 1000 documents using the default Indri QL implementation and re-rank these documents based on their expanded representations as described in Section \ref{section.model}.
 
@@
 \begin{tabular}{|c|p{0.29\textwidth}|c|} \hline
-{\bf Param} & {\bf Meaning} & {\bf Value} \\ \hline
+{\bf Param.} & {\bf Meaning} & {\bf Value} \\ \hline
 $k$ & The maximum number of document terms to use in constructing $Q_D$. & 20 \\ \hline
@@
 
-The various parameters required for our approach, along with their meanings and the values used in our experiments, are shown in Table \ref{table.parameters}.
+The parameters required for our approach, their meanings, and the values used in our experiments are shown in Table \ref{table.parameters}.
 
@@
 
-Retrieval performance for various runs are shown in Table \ref{table.performance}.
-We use mean average precision (MAP) and normalized discounted cumulative gain at 20 (nDCG@20) to measure performance.
-Each metric has been optimized with 10-fold cross-validation.
+Retrieval performance of each run is shown in Table \ref{table.performance}.
+We measure performance with mean average precision (MAP) and normalized discounted cumulative gain at 20 (nDCG@20).
+Each metric is optimized with 10-fold cross-validation.
 
-The results confirm that document expansion provides benefit over a baseline query likelihood run---no run performs significantly worse than the baseline, and most runs improve over the baseline query likelihood run.
+The results confirm that document expansion provides benefit over a baseline query likelihood run---no run performs significantly worse than the baseline, and most runs improve over the baseline QL run.
 % Note that baselines correspond to $\sum_{j=1}^n \lambda_{{\mathcal{E}_D}_j} = 0.0$.
@@
 Performance of RM3 runs is more surprising with improvement over the baseline RM3 occurring more rarely compared to improvement over the baseline QL.
-The data suggest that RM3 runs may be more effective in more heterogeneous collections: there are three RM3 improvements in Robust and six in wt10g, compared to only one in AP.
+The data suggest that RM3 runs may be more effective in more heterogeneous collections: there are three RM3 improvements in robust and six in wt10g, compared to only one in AP.
 This makes intuitive sense since a homogeneous collection would be expected to receive less benefit from query expansion.
@@
 In general, \textit{wiki} runs perform similarly to \textit{double} runs.
-However, the strong performance of \textit{double} runs \textit{is} visible when query expansion is ignored: five out of six \textit{double} QL runs show statistically significant improvement over \textit{wiki} QL runs.
+However, the strong performance of \textit{double} runs is visible when query expansion is ignored: five out of six \textit{double} QL runs show statistically significant improvement over \textit{wiki} QL runs.
 In one case (wt10g measuring nDCG@20) the \textit{double} QL run even outperforms the \textit{wiki} RM3 run with statistical significance.
@@
 
-Figure \ref{figure.n-sweeps} shows sweeps over several values of $n$, the number of expansion documents, for each target collection using our established 10-fold cross-validation procedure with identical folds.
+Figure \ref{figure.n-sweeps} shows sweeps over several values of $n$, the number of expansion documents, for each target collection using our established cross-validation procedure with identical folds.
 The sensitivity to $n$ is not pronounced at $n \geq 5$, and what little variation exists is not consistent across collections.
@@
 
-The results indicate that our approach for expanding documents using Wikipedia and the document's original collection produces useful data for document retrieval purposes.
-Our simple document expansion model performs well compared to both a query likelihood and RM3 baseline.
+The results indicate that our approach for document expansion work well in general and especially in concert with traditional relevance modeling techniques.
+We find that we can improve on traditional document expansion by incorporating external collections into the expansion process.
+In the future, we plan to investigate in detail the relationship between homogeneity of documents and the performance of our model.
 

### 2017-02-18 paper.tex
clarified section on sensitivity to n

@@
 
-Figure \ref{figure.n-sweeps} shows sweeps over several values of $n$, the number of expansion documents, for each target collection using our established cross-validation procedure with identical folds.
+Figure \ref{figure.n-sweeps} shows sweeps over several values of $n$, the number of expansion documents, for the \textit{single} and \textit{wiki} QL runs using our established cross-validation procedure with identical folds.
 The sensitivity to $n$ is not pronounced at $n \geq 5$, and what little variation exists is not consistent across collections.
-We therefore choose the value of 10 as an apparently safe value; this is a convenient result since it allows for more efficient document expansion.
+We therefore set the value of 10, an apparently safe value, for all other runs.
+This is a convenient result since it allows for more efficient document expansion.
 

### 2017-02-20 paper.tex
updated with feedback from Craig, added wiki sweeps over n

@@
 \usepackage{array}
+\usepackage{bm}
 \usepackage{booktabs}
@@
 \begin{abstract}
-Document expansion has been shown to improve the performance of information retrieval systems by augmenting documents' term probability estimates with those of similar documents, producing higher quality document representations.
+Document expansion has been shown to improve the effectiveness of information retrieval systems by augmenting documents' term probability estimates with those of similar documents, producing higher quality document representations.
 We propose a method to further improve document models by utilizing external collections as part of the document expansion process.
 Our approach is based on relevance modeling, a popular form of pseudo-relevance feedback; however, where relevance modeling is concerned with \textit{query} expansion, we are concerned with \textit{document} expansion.
-Our experiments demonstrate that the proposed model improves ad-hoc document retrieval performance on a variety of corpus types, with a particular benefit on more heterogeneous collections of documents.
+Our experiments demonstrate that the proposed model improves ad-hoc document retrieval effectiveness on a variety of corpus types, with a particular benefit on more heterogeneous collections of documents.
 \end{abstract}
@@
 
-Because relevance models are prone to query drift, it is often desirable to linearly interpolate an RM with the original query model to improve performance:
+Because relevance models are prone to query drift, it is often desirable to linearly interpolate an RM with the original query model to improve effectiveness:
 
@@
 	\item Wikipedia, called \textit{wiki}; or
-	\item a mixture of the previous two, called \textit{double}.
+	\item a mixture of the previous two, called \textit{combined}.
 \end{itemize}
@@
 In principle, this parameter need not be limited beyond the length of the document; however, this would increase computation time significantly, so we have set it to a reasonable value.
-The parameter $n$ is also set heuristically; see Section \ref{section.n-sensitivity} for a discussion of the performance sensitivity to the setting of $n$.
+The parameter $n$ is also set heuristically; see Section \ref{section.n-sensitivity} for a discussion of the sensitivity of our model to the setting of $n$.
 
@@
 \includegraphics[width=\linewidth]{figures/expansion-sweep.pdf}
-\caption{Sweeps over values of $n$, the number of expansion documents.}
+\caption{Sweeps over the number of expansion documents, $n = \{0, 1, 5, 10, 50\}$, for the \textit{self} and \textit{wiki} QL runs.}
 \label{figure.n-sweeps}
@@
 {\bf Corpus} & {\bf \bigcell{l}{Exp. \\ Source}} & {\bf Run} & {\bf MAP} & {\bf nDCG@20} \\ \hline\hline
+
 \rule{0pt}{2.5ex} \multirow{8}{*}{AP} & \cellcolor{gray!50} & \cellcolor{gray!50}{\it QL} & \cellcolor{gray!50}0.2337 & \cellcolor{gray!50}0.4170 \\ \cline{3-5}
-\rule{0pt}{2.5ex} & \cellcolor{gray!50} \multirow{-2}{*}{\it Baseline} & \cellcolor{gray!50}{\it RM3} & \cellcolor{gray!50}0.3310$^\uparrow$ & \cellcolor{gray!50}0.4855$^\uparrow$ \\ \cline{2-5}
-\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Self} & {\it QL} & 0.2694$^\uparrow$ & 0.4519$^\uparrow$ \\ \cline{3-5}
-\rule{0pt}{2.5ex} & & {\it RM3} & 0.3295$^{\uparrow *}$ & \textbf{0.4876}$^{\uparrow *}$ \\ \cline{2-5}
-\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Wiki} & {\it QL} & 0.2644$^\uparrow$ & 0.4582$^\uparrow$ \\ \cline{3-5}
-\rule{0pt}{2.5ex} & & {\it  RM3} & 0.3334$^{\uparrow *}$ & 0.4811$^{\uparrow *}$ \\ \cline{2-5}
-\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Double} & {\it QL} & 0.2774$^{\uparrow SW}$ & 0.4734$^{\uparrow SW}$ \\ \cline{3-5}
-\rule{0pt}{2.5ex} & & {\it RM3} & \textbf{0.3342}$^{\uparrow\Uparrow *S}$ & 0.4789$^\uparrow$ \\ \hline\hline
+\rule{0pt}{2.5ex} & \cellcolor{gray!50} \multirow{-2}{*}{\it Baseline} & \cellcolor{gray!50}{\it RM3} & \cellcolor{gray!50}0.3310$^{\underline{\uparrow}}$ & \cellcolor{gray!50}0.4855$^{\underline{\uparrow}}$ \\ \cline{2-5}
+\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Self} & {\it QL} & 0.2694$^{\underline{\uparrow}}$ & 0.4519$^{\underline{\uparrow}}$ \\ \cline{3-5}
+\rule{0pt}{2.5ex} & & {\it RM3} & 0.3295$^{\underline{\uparrow *}}$ & \textbf{0.4876}$^{\underline{\uparrow *} W}$ \\ \cline{2-5}
+\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Wiki} & {\it QL} & 0.2644$^{\underline{\uparrow}}$ & 0.4582$^{\underline{\uparrow}}$ \\ \cline{3-5}
+\rule{0pt}{2.5ex} & & {\it  RM3} & 0.3334$^{\underline{\uparrow *}}$ & 0.4811$^{\underline{\uparrow} *}$ \\ \cline{2-5}
+\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Combined} & {\it QL} & 0.2774$^{\underline{\uparrow W}S}$ & 0.4734$^{\underline{\uparrow SW}}$ \\ \cline{3-5}
+\rule{0pt}{2.5ex} & & {\it RM3} & \textbf{0.3342}$^{\underline{\uparrow *}\Uparrow S}$ & 0.4789$^{\underline{\uparrow}}$ \\ \hline\hline
+
 \rule{0pt}{2.5ex} \multirow{8}{*}{Robust} & \cellcolor{gray!50} & \cellcolor{gray!50}{\it QL} & \cellcolor{gray!50}0.2183 & \cellcolor{gray!50}0.3867 \\ \cline{3-5}
-\rule{0pt}{2.5ex} & \cellcolor{gray!50} \multirow{-2}{*}{\it Baseline} & \cellcolor{gray!50}{\it RM3} & \cellcolor{gray!50}0.2639$^\uparrow$ & \cellcolor{gray!50}0.3908 \\ \cline{2-5}
-\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Self} & {\it QL} & 0.2369$^\uparrow$ & 0.4036$^\uparrow$ \\ \cline{3-5}
-\rule{0pt}{2.5ex} & & {\it RM3} & 0.2591$^{\uparrow\Downarrow *}$ & 0.3894$^{*}$ \\ \cline{2-5}
-\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Wiki} & {\it QL} & 0.2326$^\uparrow$ & 0.4040$^\uparrow$ \\ \cline{3-5}
-\rule{0pt}{2.5ex} & & {\it RM3} & \textbf{0.2674}$^{\uparrow *}$ & 0.4201$^{\uparrow\Uparrow *}$ \\ \cline{2-5}
-\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Double} & {\it QL} & 0.2417$^{\uparrow W}$ & 0.4156$^{\uparrow\Uparrow SW}$ \\ \cline{3-5}
-\rule{0pt}{2.5ex} & & {\it RM3} & 0.2672$^{\uparrow *S}$ & \textbf{0.4205}$^{\uparrow\Uparrow S}$ \\ \hline\hline
+\rule{0pt}{2.5ex} & \cellcolor{gray!50} \multirow{-2}{*}{\it Baseline} & \cellcolor{gray!50}{\it RM3} & \cellcolor{gray!50}0.2639$^{\underline{\uparrow}}$ & \cellcolor{gray!50}0.3908$^{\underline{\uparrow}}$ \\ \cline{2-5}
+\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Self} & {\it QL} & 0.2369$^{\underline{\uparrow}}$ & 0.4036$^{\underline{\uparrow}}$ \\ \cline{3-5}
+\rule{0pt}{2.5ex} & & {\it RM3} & 0.2591$^{\underline{\uparrow\Downarrow *}}$ & 0.3894$^{*}$ \\ \cline{2-5}
+\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Wiki} & {\it QL} & 0.2326$^{\underline{\uparrow}}$ & 0.4040$^\uparrow$ \\ \cline{3-5}
+\rule{0pt}{2.5ex} & & {\it RM3} & \textbf{0.2674}$^{\underline{\uparrow *S}}$ & 0.4201$^{\underline{\uparrow\Uparrow S} *}$ \\ \cline{2-5}
+\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Combined} & {\it QL} & 0.2417$^{\underline{\uparrow W}}$ & 0.4156$^{\underline{\uparrow\Uparrow W} S}$ \\ \cline{3-5}
+\rule{0pt}{2.5ex} & & {\it RM3} & 0.2672$^{\underline{\uparrow *S}}$ & \textbf{0.4205}$^{\underline{\uparrow\Uparrow S}}$ \\ \hline\hline
+
 \rule{0pt}{2.5ex} \multirow{8}{*}{wt10g} & \cellcolor{gray!50} & \cellcolor{gray!50}{\it QL} & \cellcolor{gray!50}0.1683 & \cellcolor{gray!50}0.2816 \\ \cline{3-5}
-\rule{0pt}{2.5ex} & \cellcolor{gray!50} \multirow{-2}{*}{\it Baseline} & \cellcolor{gray!50}{\it RM3} & \cellcolor{gray!50}0.1651 & \cellcolor{gray!50}0.2834 \\ \cline{2-5}
+\rule{0pt}{2.5ex} & \cellcolor{gray!50} \multirow{-2}{*}{\it Baseline} & \cellcolor{gray!50}{\it RM3} & \cellcolor{gray!50}0.1651 & \cellcolor{gray!50}0.2834$^{\underline{\uparrow}}$ \\ \cline{2-5}
 \rule{0pt}{2.5ex} & \multirow{2}{*}{\it Self} & {\it QL} & 0.1660 & 0.2936 \\ \cline{3-5}
 \rule{0pt}{2.5ex} & & {\it RM3} & 0.1694$^\Uparrow$ & 0.2758$^\Downarrow$ \\ \cline{2-5}
-\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Wiki} & {\it QL} & 0.1780$^\uparrow$ & 0.3029$^\uparrow$ \\ \cline{3-5}
-\rule{0pt}{2.5ex} & & {\it RM3} & \textbf{0.2089}$^{\uparrow\Uparrow *}$ & \textbf{0.3085}$^{\uparrow\Uparrow}$ \\ \cline{2-5}
-\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Double} & {\it QL} & 0.1759$^{S}$ & 0.3148$^{\uparrow\Uparrow SW}$ \\ \cline{3-5}
-\rule{0pt}{2.5ex} & & {\it RM3} & 0.2061$^{\uparrow\Uparrow *S}$ & 0.3082$^{\uparrow\Uparrow S}$ \\ \hline
+\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Wiki} & {\it QL} & 0.1780$^{\uparrow \underline{S}}$ & 0.3029$^\uparrow$ \\ \cline{3-5}
+\rule{0pt}{2.5ex} & & {\it RM3} & \textbf{0.2089}$^{\underline{\uparrow\Uparrow *S}}$ & \textbf{0.3085}$^{\underline{\uparrow S}\Uparrow}$ \\ \cline{2-5}
+\rule{0pt}{2.5ex} & \multirow{2}{*}{\it Combined} & {\it QL} & 0.1759$^{\uparrow\Uparrow S}$ & 0.3148$^{\underline{\uparrow\Uparrow} SW}$ \\ \cline{3-5}
+\rule{0pt}{2.5ex} & & {\it RM3} & 0.2061$^{\underline{\uparrow\Uparrow *S}}$ & 0.3082$^{\underline{\uparrow\Uparrow S}}$ \\ \hline
 \end{tabular}
 \caption{Performance of runs using various expansion sources with (\textit{RM3}) and without (\textit{QL}) query expansion.
-Statistical significance at $p \leq 0.05$ is marked with a variety of symbols: $\uparrow$ indicates improvement over the baseline QL run; $\Uparrow$ and $\Downarrow$ indicate improvement and decline respectively with respect to the baseline RM3 run; $^{*}$ indicates improvement over the QL run with the same expansion source; $^{S}$ and $^{W}$ indicate improvement over the \textit{self} and \textit{wiki} sources, respectively, of the same run type.
+Statistical significance at $p \leq 0.05$ is marked with a variety of symbols; underlining further designates $p \leq 0.01$: $\uparrow$ indicates improvement over the baseline QL run; $\Uparrow$ and $\Downarrow$ indicate improvement and decline respectively with respect to the baseline RM3 run; $^{*}$ indicates improvement over the QL run with the same expansion source; $^{S}$ and $^{W}$ indicate improvement over the \textit{self} and \textit{wiki} sources, respectively, of the same run type.
 Bolded runs are the highest raw score for an evaluation metric in a given collection.}
-\label{table.performance}
+\label{table.effectiveness}
 \end{table}
 
-Retrieval performance of each run is shown in Table \ref{table.performance}.
-We measure performance with mean average precision (MAP) and normalized discounted cumulative gain at 20 (nDCG@20).
+Retrieval effectiveness of each run is shown in Table \ref{table.effectiveness}.
+We measure effectiveness with mean average precision (MAP) and normalized discounted cumulative gain at 20 (nDCG@20).
 Each metric is optimized with 10-fold cross-validation.
@@
 
-In general, \textit{wiki} runs perform similarly to \textit{double} runs.
-However, the strong performance of \textit{double} runs is visible when query expansion is ignored: five out of six \textit{double} QL runs show statistically significant improvement over \textit{wiki} QL runs.
-In one case (wt10g measuring nDCG@20) the \textit{double} QL run even outperforms the \textit{wiki} RM3 run with statistical significance.
+In general, \textit{wiki} runs perform similarly to \textit{combined} runs.
+However, the strong performance of \textit{combined} runs is visible when query expansion is ignored: five out of six \textit{combined} QL runs show statistically significant improvement over \textit{wiki} QL runs.
+In one case (wt10g measuring nDCG@20) the \textit{combined} QL run even outperforms the \textit{wiki} RM3 run with statistical significance.
 
@@
 
-Figure \ref{figure.n-sweeps} shows sweeps over several values of $n$, the number of expansion documents, for the \textit{single} and \textit{wiki} QL runs using our established cross-validation procedure with identical folds.
+Figure \ref{figure.n-sweeps} shows sweeps over several values of $n$, the number of expansion documents, for the \textit{self} and \textit{wiki} QL runs using our established cross-validation procedure with identical folds.
 The sensitivity to $n$ is not pronounced at $n \geq 5$, and what little variation exists is not consistent across collections.
@@
 We find that we can improve on traditional document expansion by incorporating external collections into the expansion process.
-In the future, we plan to investigate in detail the relationship between homogeneity of documents and the performance of our model.
+In the future, we plan to investigate in detail the relationship between homogeneity of documents and the effectiveness of our model.
 

### 2017-02-25 qpp/paper.tex
added QPP paper with initial work

\documentclass{sig-alternate}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{array}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{verbatim}
\usepackage{colortbl}
\usepackage[table]{xcolor}

\newcommand\rankeq{\mathrel{\overset{\makebox[0pt]{\mbox{\normalfont\tiny\sffamily rank}}}{=}}}
\newcommand{\bigcell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}

\setlist[itemize]{noitemsep}  % remove space between list items
\setlist[enumerate]{noitemsep}  % remove space between list items

\begin{document}

\author{Garrick Sherman}

\title{}

\maketitle
\begin{abstract}
\end{abstract}

\section{Introduction}\label{section.intro}

Query performance prediction (QPP) is the task of estimating the success of an information retrieval (IR) system in retrieving results for a submitted query. Prediction strategies generally use properties of the query or of the retrieved document set to quantify the success of a system. The former is called pre-retrieval prediction, while the latter is called post-retrieval prediction. On the whole, post-retrieval prediction outperforms pre-retrieval prediction, and our predictor belongs to this class.

In general, post-retrieval prediction methods tend to associate some property of the result set with the relevance of the result set in general (or, more accurately, some measurement thereof). These properties are usually intuitively suggestive of some form of stability or robustness, as discussed in Section \ref{section.related}.

In this work, we propose a predictor inspired by pseudo-relevance feedback techniques that directly incorporates relevance metrics in the prediction process. We accomplish this by asserting that the top $r$ retreived documents in a ranked list for a query $Q$ are relevant to that query; we then use these pseudo-relevance judgments to estimate document retrieval evaluation using natural variations on the query: the top $n$ ranked documents.

\section{Related Work}\label{section.related}

A great deal of research has focused on QPP. The most famous predictor is query clarity, which is simply the KL-divergence of an expanded query model and the collection as a whole \cite{Cronen-Townsend2002}. We incorporate query clarity as a baseline in our work.

One class of query performance predictor that is related to our work is query perturbation \cite{Vinay2006, Yom-Tov2005, Zhou2007}. These methods alter the query and measure the similarity of the results list across query variations; if the result list remains relatively constant, the system is believed to have little difficulty with the query. Our proposed method is fundamentally a form of query perturbation, with the alternative query forms derived from feedback documents.

\section{Pseudo-Relevance Performance Predictor}\label{section.method}

Our query performance predictor, which we call the pseudo-relevance performance predictor (PRPP), is inspired by the pseudo-relevance feedback technique of treating the top ranked documents as relevant to the query. Doing so allows us to directly model the robustness of query performance metrics to query perturbation. The broad steps of our approach are as follows:

\begin{enumerate}
	\item Issue query $Q$ against collection $C_p$; call the results list $R_p$
	\item Record the top $r$ documents in $R_p$ as relevant using each's normalized retrieval score as the degree of relevance
	\item Issue $Q$ against target collection $C_t$, if $C_p \neq C_t$; call the results list $R_t$
	\item For each document $D$ in $R_t$,
	\begin{enumerate}
		\item Construct a pseudo-query $Q_D$ consisting of the top $q$ non-stop terms\footnote{We remove terms in the standard Indri stoplist: http://www.lemurproject.org/stopwords/stoplist.dft} in $D$
		\item Issue $Q_D$ against $C_p$; call the results list $R_{pD}$
		\item Score $R_{pD}$ using the pseudo-relevance judgments from Step 2.
	\end{enumerate}
	\item Average the scores to compute a single score for $Q$
\end{enumerate}

\noindent Several points in the preceding would benefit from clarification.

First, our model makes no assertions about the identity of the performance collection $C_p$. While it is valid to use the target collection as the performance collection, we hypothesize that the use of an external collection may yield better results. We investigate this idea in Section \ref{section.experiments}.

Next, both $r$ and $q$ are free parameters in our approach. In fact, there are two other parameters in our approach: $k$ controls the length of $R_t$, while $n$ controls the length of $R_{pD}$. In general, all parameters should be set empirically. Although not required mathematically, we only allow values of $n$ where $n \leq r$ since setting $n$ greater than $r$ prevents us from retrieving all relevant documents.

One advantage to our model is the ability to predict specific retrieval metrics by estimating levels of relevance. Because these levels are normalized log probabilities, they consist of continuous values (in contrast to TREC qrels which contain binary or discrete relevance grades), but are still valid for metrics that incorporate graded relevance judgments like normalized discounted cumulative gain (nDCG). Metrics that use only binary relevance metrics, like mean average precision (MAP) follow the typical procedure of treating all judgments greater than zero as relevant.

\section{Evaluation}\label{section.evaluation}

\subsection{Data}\label{section.evaluation.data}

We evaluate our procedure using a variety of TREC datasets that represent a variety of corpora properties:

\begin{itemize}
	\item AP newsire with topics 101-200 from TREC disks 1 and 2
	\item Robust with the 2004 topics from TREC disks 4 and 5
	\item wt10g with the topics 451-500 from the 2000 and 2001 TREC Web tracks
\end{itemize}

We also make use of Wikipedia\footnote{http://en.wikipedia.org} as an external collection in some experiments.

% \subsection{Parameters}\label{section.evaluation.runs}

% Our predictor requires the setting of several parameters. We set $r$, $k$, and $n$ by 10-fold cross-validation: we sweep over each parameter at the values $\{1, 5, 10, 20, 50, 75, 100\}$; as noted in Section \ref{section.method}, $n$ is only swept at values $\leq r$. We set $q = 20$ for all runs since using the entire length of $D$, $|D|$, is excessively expensive during retrieval.

% We follow a typical cross-validation procedure, as follows. We split the batch of test queries into ten folds. All runs use the same random division of queries to ensure fair comparisons. For each fold, we evaluate the training queries at each parameter setting and determine which yields the highest correlation with the target metric (e.g. MAP or nDCG). We then apply the optimal parameter setting to the test queries. By concatenating each fold of test queries, we produce a single test run comprising all queries in the batch, on which we can then run a final correlation to evaluate our predictor.

% We perform the same procedure on the parameters involved in our baseline predictors, which are discussed in more detail in Section \ref{section.results}.

\section{Results}\label{section.results}

% \begin{table}
% \begin{tabular}{|l|l|c|c|c|c|} \hline\hline
% & & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \hline\hline
% Corpus & Predictor & Pearson & Kendall & Pearson & Kendall \\ \hline\hline
% \multirow{3}{*}{AP} & Query clarity & 0.3936 & \textbf{0.3627} & 0.1267 & 0.1194 \\ \cline{2-6}
% & Query feedback & 0.4244 & 0.3010 & \textbf{0.4467} & 0.3100 \\ \cline{2-6}
% & PRPP & \textbf{0.5575} & 0.2904 & 0.1720 & \textbf{0.3110} \\ \hline\hline
% \multirow{3}{*}{wt10g} & Query clarity & 0.2206 & 0.2606 & 0.3436 & 0.2622 \\ \cline{2-6}
% & Query feedback & 0.3847 & 0.2327 & 0.2921 & 0.1860 \\ \cline{2-6}
% & PRPP & -0.0132 & 0.3307 & 0.1695 & 0.2046 \\ \hline\hline
% \multirow{3}{*}{Robust} & Query clarity & 0.4451 & 0.3681 & 0.2427 & 0.2821 \\ \cline{2-6}
% & Query feedback & 0.4685 & 0.3112 & 0.4526 & 0.3073 \\ \cline{2-6}
% & PRPP & \textbf{0.5438} & 0.3874 & 0.2232 & 0.3323 \\ \hline\hline
% \end{tabular}
% \caption{Performance of predictors with Pearson's $r$ and Kendall's $\tau$ correlation.}
% \label{table.results.self}
% \end{table}
% 
% \begin{table}
% \begin{tabular}{|l|c|c|c|c|} \hline\hline
% & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \hline\hline
% Predictor & Pearson & Kendall & Pearson & Kendall \\ \hline\hline
% Query clarity &  &  &  &  \\ \hline\hline
% Query feedback &  &  &  &  \\ \hline\hline
% PRPP &  &  &  &  \\ \hline\hline
% \end{tabular}
% \caption{Performance of predictors with Pearson's $r$ and Kendall's $\tau$ correlation using Wikipedia.}
% \label{table.results.self}
% \end{table}

\begin{table}
\begin{tabular}{|l|l|c|c|c|c|} \hline
& & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{3-6}
Corpus & Pred. & Med. & Max & Med. & Max \\ \hline\hline
\multirow{3}{*}{AP} & QC & \textbf{0.5280} & \textbf{0.6148} & 0.3564 & 0.4284 \\ \cline{2-6}
& QF & 0.4240 & 0.5637 & 0.3202 & 0.4467 \\ \cline{2-6}
& PRPP & 0.5030 & 0.6115 & \textbf{0.4025} & \textbf{0.4880} \\ \hline\hline
\multirow{3}{*}{wt10g} & QC & 0.2232 & 0.3636 & 0.0943 & 0.3436 \\ \cline{2-6}
& QF & 0.1624 & 0.3847 & 0.0881 & 0.3613 \\ \cline{2-6}
& PRPP & \textbf{0.2850} & \textbf{0.4615} & \textbf{0.2529} & \textbf{0.4173} \\ \hline\hline
\multirow{3}{*}{Robust} & QC & 0.4240 & 0.5114 & 0.3129 & 0.3914 \\ \cline{2-6}
& QF & 0.2203 & 0.5073 & 0.1708 & 0.4926 \\ \cline{2-6}
& PRPP & \textbf{0.4381} & \textbf{0.5791} & \textbf{0.3222} & \textbf{0.5047} \\ \hline
\end{tabular}
\caption{Median and maximum Pearson's $r$ correlation of predictors for each collection. Bolded values are the largest observed per corpus/metric summary.}
\label{table.results.self.pearson}
\end{table}

\begin{table}
\begin{tabular}{|l|l|c|c|c|c|} \hline
& & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{3-6}
Corpus & Pred. & Med. & Max & Med. & Max \\ \hline\hline
\multirow{3}{*}{AP} & QC & 0.3609 & 0.4440 & 0.2166 & 0.2807 \\ \cline{2-6}
& QF & 0.3259 & 0.4215 & 0.2042 & 0.3100 \\ \cline{2-6}
& PRPP & \textbf{0.4132} & \textbf{0.4962} & \textbf{0.2701} & \textbf{0.3378} \\ \hline\hline
\multirow{3}{*}{wt10g} & QC & 0.1561 & 0.3093 & 0.0712 & 0.2622 \\ \cline{2-6}
& QF & 0.1599 & 0.2843 & 0.0657 & 0.2411 \\ \cline{2-6}
& PRPP & \textbf{0.2710} & \textbf{0.3642} & \textbf{0.1935} & \textbf{0.3053} \\ \hline\hline
\multirow{3}{*}{Robust} & QC & 0.2985 & 0.3714 & 0.2266 & 0.2889 \\ \cline{2-6}
& QF & 0.1895 & 0.3745 & 0.1389 & \textbf{0.3646} \\ \cline{2-6}
& PRPP & \textbf{0.3433} & \textbf{0.4273} & \textbf{0.2478} & 0.3634 \\ \hline
\end{tabular}
\caption{Median and maximum Kendall's $\tau$ correlation of predictors for each correlation. Bolded values are the largest observed per corpus/metric summary.}
\label{table.results.self.kendall}
\end{table}

\section{Conclusions}\label{section.conclusions}

\section{Acknowledgments}\label{section.acknowledgments}

This work was supported in part by the US National Science Foundation under Grant No. [blind]. Any opinions, findings, conclusions, or recommendations expressed are those of the authors and do not necessarily reflect the views of the National Science Foundation.

\bibliographystyle{abbrv}
\bibliography{library}

\end{document}

### 2017-02-26 expansion/paper.tex
added QPP paper with initial work
page limit and small fixes

--- 2017-02-20 paper.tex
@@
 
-\author{Garrick Sherman}
+%\author{Garrick Sherman}
+\author{[Blind]}
 
@@
 \begin{flalign}\label{equation.ql}
-\log P(Q | D) = \prod_{w \in Q} P(w | Q) \cdot \log P(w | \theta_D) .
+P(Q | D) = \prod_{w \in Q} P(w | \theta_D)^{c(w,Q)}
 \end{flalign}
 
-\noindent We follow standard procedures for estimating the probabilities in Eq.
-\ref{equation.ql}.
-We simply use the maximum likelihood estimate of $\hat{P}(w | Q) = \frac{c(w, Q)}{|Q|}$ where $c(w, Q)$ is the frequency of word $w$ in $Q$.
-For $P(w | \theta_D)$ we estimate a smoothed language model by assuming that document language models
-in a given collection have a Dirichlet prior distribution:
+\noindent where $c(w, Q)$ is the frequency of word $w$ in $Q$.
+We follow standard procedures for estimating $P(w|\theta_D)$ in Eq.
+\ref{equation.ql}, estimating a smoothed language model by assuming that document language models in a given collection have a Dirichlet prior distribution:
 
@@
 
-A relevance model takes the form of
+Assuming uniform document prior probabilities, relevance models take the form of
 
 \begin{flalign}\label{equation.rm1}
-	P(w|R) = \sum_{D \in C} P(D) P(w|D) P(Q|D)
+	P(w|R) = \sum_{D \in C} P(w|D) P(Q|D)
 \end{flalign}
@@
 \ref{equation.ql} and essentially weights word $w$ in $D$ by the query likelihood of the document.
-Relevance models are most efficient and robust when calculated over only the top terms in only the top ranked documents.
-These parameters are referred to as $fbTerms$ and $fbDocs$ respectively in Table \ref{table.parameters}.
+Relevance models are most efficient and robust when calculated over only the top ranked documents and limited to the top terms.
+These parameters are referred to as $fbDocs$ and $fbTerms$ respectively in Table \ref{table.parameters}.
 
@@
 
-We obtain a ranking of related documents, which we call expansion documents, by running $Q_D$ over an index $C_E$.
+We rank related documents, called expansion documents, by running $Q_D$ over an index $C_E$.
 More formally, we rank the documents in $C_E$ against $D$ using Eq.
-\ref{equation.ql}, substituting $Q_D$ for the query and $E_i$---the text of the $i^{th}$ expansion document---for the document.
+\ref{equation.ql}, substituting $Q_D$ for the query and $E_i$---the $i^{th}$ expansion document---for the document.
 Let $\pi_i$ be the log-probability for expansion document $E_i$ with respect to $D$ given by Eq.
@@
 
-\subsubsection{Expansion Source}\label{section.evaluation.runs.expansion}
-
-We test each type of expansion source individually, with documents expanded using:
+We produce runs with expansion documents from:
 \begin{itemize}
+	\item the target collection itself, called \textit{self};
+	\item Wikipedia, called \textit{wiki};
+	\item a mixture of the previous two, called \textit{combined}; or
 	\item no expansion, called \textit{baseline};
-	\item the target collection itself, called \textit{self};
-	\item Wikipedia, called \textit{wiki}; or
-	\item a mixture of the previous two, called \textit{combined}.
 \end{itemize}
@@
 The sensitivity to $n$ is not pronounced at $n \geq 5$, and what little variation exists is not consistent across collections.
-We therefore set the value of 10, an apparently safe value, for all other runs.
+We therefore set $n$ to 10, an apparently safe value, for all other runs.
 This is a convenient result since it allows for more efficient document expansion.
@@
 
-The results indicate that our approach for document expansion work well in general and especially in concert with traditional relevance modeling techniques.
+The results indicate that our approach for document expansion works well in general and especially in concert with traditional relevance modeling.
 We find that we can improve on traditional document expansion by incorporating external collections into the expansion process.
@@
 
-\section{Acknowledgments}\label{section.acknowledgments}
-This work was supported in part by the US National Science Foundation under Grant No.
+%\section{Acknowledgments}\label{section.acknowledgments}
+
+%This work was supported in part by the US National Science Foundation under Grant No.
 [blind].

### 2017-02-27 qpp/paper.tex
bunch of work

@@
 
-\author{Garrick Sherman}
+\author{[Blind]}
 
-\title{}
+\title{Pseudo-Relevance Query Performance Prediction for Information Retrieval}
 
@@
 
-A great deal of research has focused on QPP.
-The most famous predictor is query clarity, which is simply the KL-divergence of an expanded query model and the collection as a whole \cite{Cronen-Townsend2002}.
-We incorporate query clarity as a baseline in our work.
+A great deal of research has focused on QPP \cite{Carmel2010}.
+The most famous predictor is query clarity (QC) \cite{Cronen-Townsend2002}.
+Clarity is simply the KL-divergence of an expanded query language model and the collection as a whole:
+
+\begin{flalign}\label{eq.clarity}
+\sum_{w \in V} P(w|Q) \log \frac{P(w|Q)}{P(w|C)}
+\end{flalign}
+
+\noindent where $w$ is a term in the vocabulary $V$, $P(w|C)$ is the maximum likelihood estimate of $w$ in collection $C$, and $P(w|Q)$ is the probability of $w$ as computed by a relevance model \cite{Lavrenko2001}.
+
+%The latter are computed by
+
+% \begin{flalign}\label{eq.rm}
+% \sum_{D \in C} P(w|D) P(Q|D).
+% \end{flalign}
+% 
+% \noindent $P(Q|D)$ is computed as in Eq.
+
+The idea underlying clarity is that a query whose top ranked documents are linguistically distinct from a generic background language model has likely done a better job identifying relevant documents than one whose top ranked documents resemble the background model.
+Several modifications of query clarity have been proposed, e.g.
+\cite{Diaz2004, Hauff2008, He2004}.
+We incorporate traditional query clarity as a baseline in our work.
 
@@
 
+Zhou \& Croft's query feedback (QF) technique constructs a new query from the top ranked documents \cite{Zhou2007}.
+First, QF issues $Q$ against collection $C$, retrieving a results list $L$.
+By ranking each term $w$ in $L$ according to its contribution to query clarity (that is, its contribution to the KL-divergence with the collection) and selecting the top ranked terms, a new query $Q'$ is constructed.
+After retrieving results list $L'$ for $Q'$, the percentage overlap between $L$ and $L'$ is computed.
+This overlap is the QF score.
+This technique bears a resemblance to our proposed method: like ours, the top ranked results give rise to alternate queries, and the results lists of the original and alternate queries are compared.
+Unlike ours, however, QF produces only a single alternate query; our method also differs in its scoring component, which directly models retrieval performance rather than simply measuring overlap as QF does.
+Because of its similarity to our method, we use query feedback as a second baseline.
+
 \section{Pseudo-Relevance Performance Predictor}\label{section.method}
+
+\subsection{Underlying Retrieval Model}\label{section.method.underlying}
+
+In this paper, we employ the standard multinomial query likelihood (QL) retrieval model to rank the relevance of a document $D$ to query $Q$, although it should be noted that this model is not required by our query performance predictor.
+
+Assuming a uniform distribution over documents, QL scores $D$ by the following:
+
+\begin{flalign}\label{eq.ql}
+P(Q|D) = \prod_{i=1}^{|Q|} P(q_i|\theta_D)
+\end{flalign}
+
+\noindent where $q_i$ is a word in $Q$ and $P(q_i|\theta_D)$ is estimated using Dirichlet smoothing:
+
+\begin{flalign}\label{eq.dirichlet}
+P(q_i|\theta_D) = \frac{c(q_i,D) + \mu \hat{P}(q_i|C)}{|D| + \mu}
+\end{flalign}
+
+\noindent where $c(q_i,D)$ is the frequency of $q_i$ in $D$, $|D|$ is the length of the document, $\hat{P}(q_i|C)$ is the maximum likelihood estimate of $q_i$ in collection $C$, and $\mu$ is a parameter.
+We set $\mu = 2500$ for all runs.
+
+\subsection{Predicting Query Performance}\label{section.method.predicting}
 
@@
 % \begin{table}
-% \begin{tabular}{|l|l|c|c|c|c|} \hline\hline
-% & & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \hline\hline
-% Corpus & Predictor & Pearson & Kendall & Pearson & Kendall \\ \hline\hline
-% \multirow{3}{*}{AP} & Query clarity & 0.3936 & \textbf{0.3627} & 0.1267 & 0.1194 \\ \cline{2-6}
-% & Query feedback & 0.4244 & 0.3010 & \textbf{0.4467} & 0.3100 \\ \cline{2-6}
-% & PRPP & \textbf{0.5575} & 0.2904 & 0.1720 & \textbf{0.3110} \\ \hline\hline
-% \multirow{3}{*}{wt10g} & Query clarity & 0.2206 & 0.2606 & 0.3436 & 0.2622 \\ \cline{2-6}
-% & Query feedback & 0.3847 & 0.2327 & 0.2921 & 0.1860 \\ \cline{2-6}
-% & PRPP & -0.0132 & 0.3307 & 0.1695 & 0.2046 \\ \hline\hline
-% \multirow{3}{*}{Robust} & Query clarity & 0.4451 & 0.3681 & 0.2427 & 0.2821 \\ \cline{2-6}
-% & Query feedback & 0.4685 & 0.3112 & 0.4526 & 0.3073 \\ \cline{2-6}
-% & PRPP & \textbf{0.5438} & 0.3874 & 0.2232 & 0.3323 \\ \hline\hline
+% \begin{tabular}{|l|l|c|c|c|c|} \hline
+% & & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{3-6}
+% Corpus & Pred. & Med. & Max & Med. & Max \\ \hline\hline
+% \multirow{4}{*}{AP} & QC & \textbf{0.5280} & \textbf{0.6148} & 0.3564 & 0.4284 \\ \cline{2-6}
+% & QF & 0.4240 & 0.5637 & 0.3202 & 0.4467 \\ \cline{2-6}
+% & PRPP-flip & 0.5020 & 0.5661 & \textbf{0.4026} & \textbf{0.5092} \\ \cline{2-6}
+% & PRPP & 0.5030 & 0.6115 & 0.4025 & 0.4880 \\ \hline\hline
+% \multirow{4}{*}{wt10g} & QC & 0.2232 & 0.3636 & 0.0943 & 0.3436 \\ \cline{2-6}
+% & QF & 0.1624 & 0.3847 & 0.0881 & 0.3613 \\ \cline{2-6}
+% & PRPP-flip & 0.2910 & 0.4665 & 0.2367 & 0.3949 \\ \cline{2-6}
+% & PRPP & \textbf{0.2850} & \textbf{0.4615} & \textbf{0.2529} & \textbf{0.4173} \\ \hline\hline
+% \multirow{4}{*}{Robust} & QC & 0.4240 & 0.5114 & 0.3129 & 0.3914 \\ \cline{2-6}
+% & QF & 0.2203 & 0.5073 & 0.1708 & 0.4926 \\ \cline{2-6}
+% & PRPP-flip & 0.3826 & 0.5743 & 0.3540 & 0.5094 \\ \cline{2-6}
+% & PRPP & \textbf{0.4381} & \textbf{0.5791} & \textbf{0.3222} & \textbf{0.5047} \\ \hline
 % \end{tabular}
-% \caption{Performance of predictors with Pearson's $r$ and Kendall's $\tau$ correlation.}
-% \label{table.results.self}
+% \caption{Median and maximum Pearson's $r$ correlation of predictors for each collection. Bolded values are the largest observed per corpus/metric summary.}
+% \label{table.results.self.pearson}
 % \end{table}
@@
 % \begin{table}
-% \begin{tabular}{|l|c|c|c|c|} \hline\hline
-% & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \hline\hline
-% Predictor & Pearson & Kendall & Pearson & Kendall \\ \hline\hline
-% Query clarity &  &  &  &  \\ \hline\hline
-% Query feedback &  &  &  &  \\ \hline\hline
-% PRPP &  &  &  &  \\ \hline\hline
+% \begin{tabular}{|l|l|c|c|c|c|} \hline
+% & & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{3-6}
+% Corpus & Pred. & Med. & Max & Med. & Max \\ \hline\hline
+% \multirow{4}{*}{AP} & QC & 0.3609 & 0.4440 & 0.2166 & 0.2807 \\ \cline{2-6}
+% & QF & 0.3259 & 0.4215 & 0.2042 & 0.3100 \\ \cline{2-6}
+% & PRPP-flip & 0.4068 & 0.4670 & \textbf{0.2769} & \textbf{0.3543} \\ \cline{2-6}
+% & PRPP & \textbf{0.4132} & \textbf{0.4962} & 0.2701 & 0.3378 \\ \hline\hline
+% \multirow{4}{*}{wt10g} & QC & 0.1561 & 0.3093 & 0.0712 & 0.2622 \\ \cline{2-6}
+% & QF & 0.1599 & 0.2843 & 0.0657 & 0.2411 \\ \cline{2-6}
+% & PRPP-flip & 0.2586 & 0.3772 & 0.2006 & 0.2844 \\ \cline{2-6}
+% & PRPP & \textbf{0.2710} & \textbf{0.3642} & \textbf{0.1935} & \textbf{0.3053} \\ \hline\hline
+% \multirow{4}{*}{Robust} & QC & 0.2985 & 0.3714 & 0.2266 & 0.2889 \\ \cline{2-6}
+% & QF & 0.1895 & 0.3745 & 0.1389 & \textbf{0.3646} \\ \cline{2-6}
+% & PRPP-flip & 0.3082 & 0.4148 & 0.2783 & 0.3698 \\ \cline{2-6}
+% & PRPP & \textbf{0.3433} & \textbf{0.4273} & \textbf{0.2478} & 0.3634 \\ \hline
 % \end{tabular}
-% \caption{Performance of predictors with Pearson's $r$ and Kendall's $\tau$ correlation using Wikipedia.}
-% \label{table.results.self}
+% \caption{Median and maximum Kendall's $\tau$ correlation of predictors for each collection. Bolded values are the largest observed per corpus/metric summary.}
+% \label{table.results.self.kendall}
 % \end{table}
@@
 & & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{3-6}
-Corpus & Pred. & Med. & Max & Med. & Max \\ \hline\hline
-\multirow{3}{*}{AP} & QC & \textbf{0.5280} & \textbf{0.6148} & 0.3564 & 0.4284 \\ \cline{2-6}
-& QF & 0.4240 & 0.5637 & 0.3202 & 0.4467 \\ \cline{2-6}
-& PRPP & 0.5030 & 0.6115 & \textbf{0.4025} & \textbf{0.4880} \\ \hline\hline
-\multirow{3}{*}{wt10g} & QC & 0.2232 & 0.3636 & 0.0943 & 0.3436 \\ \cline{2-6}
-& QF & 0.1624 & 0.3847 & 0.0881 & 0.3613 \\ \cline{2-6}
-& PRPP & \textbf{0.2850} & \textbf{0.4615} & \textbf{0.2529} & \textbf{0.4173} \\ \hline\hline
-\multirow{3}{*}{Robust} & QC & 0.4240 & 0.5114 & 0.3129 & 0.3914 \\ \cline{2-6}
-& QF & 0.2203 & 0.5073 & 0.1708 & 0.4926 \\ \cline{2-6}
-& PRPP & \textbf{0.4381} & \textbf{0.5791} & \textbf{0.3222} & \textbf{0.5047} \\ \hline
+Corpus & Pred. & Valid. & Max. & Valid. & Max \\ \hline\hline
+\multirow{4}{*}{AP} & QC & 0.4748 & 0.6148 & 0.2488* & 0.4284 \\ \cline{2-6}
+& QF & 0.5178 & 0.5637 & 0.2368* & 0.4467 \\ \cline{2-6}
+& PRPP-flip & 0.4481 & 0.5661 & 0.4334 & 0.5092 \\ \cline{2-6}
+& PRPP & 0.5003 & 0.6115 & 0.3848 & 0.4880 \\ \hline\hline
+\multirow{4}{*}{wt10g} & QC & 0.2873 & 0.3636 & 0.2271* & 0.3436 \\ \cline{2-6}
+& QF & 0.3758 & 0.3847 & 0.3937 & 0.3613 \\ \cline{2-6}
+& PRPP-flip & 0.2758* & 0.4665 & 0.0957* & 0.3949 \\ \cline{2-6}
+& PRPP & 0.2533* & 0.4615 & -0.0181* & 0.4173 \\ \hline\hline
+\multirow{4}{*}{Robust} & QC & 0.4534 & 0.5114 & 0.3768 & 0.3914 \\ \cline{2-6}
+& QF & 0.5061 & 0.5073 & 0.4884 & 0.4926 \\ \cline{2-6}
+& PRPP-flip & 0.5581 & 0.5743 & 0.4889 & 0.5094 \\ \cline{2-6}
+& PRPP & 0.5602 & 0.5791 & 0.4986 & 0.5047 \\ \hline
 \end{tabular}
@@
 Corpus & Pred. & Med. & Max & Med. & Max \\ \hline\hline
-\multirow{3}{*}{AP} & QC & 0.3609 & 0.4440 & 0.2166 & 0.2807 \\ \cline{2-6}
-& QF & 0.3259 & 0.4215 & 0.2042 & 0.3100 \\ \cline{2-6}
-& PRPP & \textbf{0.4132} & \textbf{0.4962} & \textbf{0.2701} & \textbf{0.3378} \\ \hline\hline
-\multirow{3}{*}{wt10g} & QC & 0.1561 & 0.3093 & 0.0712 & 0.2622 \\ \cline{2-6}
-& QF & 0.1599 & 0.2843 & 0.0657 & 0.2411 \\ \cline{2-6}
-& PRPP & \textbf{0.2710} & \textbf{0.3642} & \textbf{0.1935} & \textbf{0.3053} \\ \hline\hline
-\multirow{3}{*}{Robust} & QC & 0.2985 & 0.3714 & 0.2266 & 0.2889 \\ \cline{2-6}
-& QF & 0.1895 & 0.3745 & 0.1389 & \textbf{0.3646} \\ \cline{2-6}
-& PRPP & \textbf{0.3433} & \textbf{0.4273} & \textbf{0.2478} & 0.3634 \\ \hline
+\multirow{4}{*}{AP} & QC & & & & \\ \cline{2-6}
+& QF & & & & \\ \cline{2-6}
+& PRPP-flip & & & & \\ \cline{2-6}
+& PRPP & & & & \\ \hline\hline
+\multirow{4}{*}{wt10g} & QC & & & & \\ \cline{2-6}
+& QF & & & & \\ \cline{2-6}
+& PRPP-flip & & & & \\ \cline{2-6}
+& PRPP & & & & \\ \hline\hline
+\multirow{4}{*}{Robust} & QC & & & & \\ \cline{2-6}
+& QF & & & & \\ \cline{2-6}
+& PRPP-flip & & & & \\ \cline{2-6}
+& PRPP & & & & \\ \hline
 \end{tabular}
-\caption{Median and maximum Kendall's $\tau$ correlation of predictors for each correlation. Bolded values are the largest observed per corpus/metric summary.}
+\caption{Median and maximum Kendall's $\tau$ correlation of predictors for each collection. Bolded values are the largest observed per corpus/metric summary.}
 \label{table.results.self.kendall}
@@
 
+The results of our predictor as well as the two baselines are shown in Tables \ref{table.results.self.pearson} and \ref{table.results.self.kendall}; the former displays Pearson's $r$ correlation while the latter displays Kendall's $\tau$ rank correlation.
+
 \section{Conclusions}\label{section.conclusions}
-
-\section{Acknowledgments}\label{section.acknowledgments}
-
-This work was supported in part by the US National Science Foundation under Grant No.
-[blind].
-Any opinions, findings, conclusions, or recommendations expressed are those of the authors and do not necessarily reflect the views of the National Science Foundation.
 

### 2017-02-28 qpp/paper.tex
a bunch more work

@@
 While it is valid to use the target collection as the performance collection, we hypothesize that the use of an external collection may yield better results.
-We investigate this idea in Section \ref{section.experiments}.
+We investigate this idea in Section \ref{section.results.external}.
 
@@
 
-% \subsection{Parameters}\label{section.evaluation.runs}
+\subsection{Parameters}\label{section.evaluation.runs}
 
-% Our predictor requires the setting of several parameters.
-We set $r$, $k$, and $n$ by 10-fold cross-validation: we sweep over each parameter at the values $\{1, 5, 10, 20, 50, 75, 100\}$; as noted in Section \ref{section.method}, $n$ is only swept at values $\leq r$.
-We set $q = 20$ for all runs since using the entire length of $D$, $|D|$, is excessively expensive during retrieval.
+Our predictor requires the setting of several parameters.
+We set $r$, $k$, and $n$ by cross-validation: we sweep over each parameter at the values $\{1, 5, 10, 20, 50, 75, 100\}$; as noted in Section \ref{section.method}, $n$ is only swept at values $\leq r$.
+We fix $q = 20$ for all runs since using the entire length of $D$, $|D|$, is excessively expensive during retrieval.
 
-% We follow a typical cross-validation procedure, as follows.
-We split the batch of test queries into ten folds.
-All runs use the same random division of queries to ensure fair comparisons.
-For each fold, we evaluate the training queries at each parameter setting and determine which yields the highest correlation with the target metric (e.g.
-MAP or nDCG).
-We then apply the optimal parameter setting to the test queries.
-By concatenating each fold of test queries, we produce a single test run comprising all queries in the batch, on which we can then run a final correlation to evaluate our predictor.
+For each run, we split the query set into two equal sized folds and run 2-fold cross-validation, using the train fold to determine the optimal parameter settings to apply to the test fold.
+We choose an equal split over other forms of cross-validation in order to provide a relatively large number of queries to each fold, leading to more stable correlation values.
+We repeat this procedure 100 times, splitting the query set randomly each time, and average the correlation values to compute an average query performance prediction.
 
-% We perform the same procedure on the parameters involved in our baseline predictors, which are discussed in more detail in Section \ref{section.results}.
+We perform the same procedure on the parameters involved in our baseline predictors.
+Query clarity requires a single parameter: the number of feedback documents; we sweep over the values $\{10, 50, 100, 250, 500, 750, 1000\}$ for this parameter.
+Query feedback has two parameters: the number of top ranked documents in results lists $L$ and $L'$, for which we consider values of $\{10, 20, 50, 75, 100, 500\}$, and the number of terms included in the newly formed query $Q'$, for which we consider $\{3, 5, 10, 15, 20\}$.
 
@@
 
+% \begin{table}
+% \begin{tabular}{|l|l|c|c|c|c|} \hline
+% & & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{3-6}
+% Corpus & Pred. & Valid. & Max. & Valid. & Max \\ \hline\hline
+% \multirow{4}{*}{AP} & QC & 0.4748 & 0.6148 & 0.2488* & 0.4284 \\ \cline{2-6}
+% & QF & 0.5178 & 0.5637 & 0.2368* & 0.4467 \\ \cline{2-6}
+% & PRPP-flip & 0.4481 & 0.5661 & 0.4334 & 0.5092 \\ \cline{2-6}
+% & PRPP & 0.5003 & 0.6115 & 0.3848 & 0.4880 \\ \hline\hline
+% \multirow{4}{*}{wt10g} & QC & 0.2873 & 0.3636 & 0.2271* & 0.3436 \\ \cline{2-6}
+% & QF & 0.3758 & 0.3847 & 0.3937 & 0.3613 \\ \cline{2-6}
+% & PRPP-flip & 0.2758* & 0.4665 & 0.0957* & 0.3949 \\ \cline{2-6}
+% & PRPP & 0.2533* & 0.4615 & -0.0181* & 0.4173 \\ \hline\hline
+% \multirow{4}{*}{Robust} & QC & 0.4534 & 0.5114 & 0.3768 & 0.3914 \\ \cline{2-6}
+% & QF & 0.5061 & 0.5073 & 0.4884 & 0.4926 \\ \cline{2-6}
+% & PRPP-flip & 0.5581 & 0.5743 & 0.4889 & 0.5094 \\ \cline{2-6}
+% & PRPP & 0.5602 & 0.5791 & 0.4986 & 0.5047 \\ \hline
+% \end{tabular}
+% \caption{Median and maximum Pearson's $r$ correlation of predictors for each collection. Bolded values are the largest observed per corpus/metric summary.}
+% \label{table.results.self.pearson}
+% \end{table}
+
 \begin{table}
-\begin{tabular}{|l|l|c|c|c|c|} \hline
+\begin{tabular}{|l|l|l|l|l|l|} \hline
 & & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{3-6}
 Corpus & Pred. & Valid. & Max. & Valid. & Max \\ \hline\hline
-\multirow{4}{*}{AP} & QC & 0.4748 & 0.6148 & 0.2488* & 0.4284 \\ \cline{2-6}
-& QF & 0.5178 & 0.5637 & 0.2368* & 0.4467 \\ \cline{2-6}
-& PRPP-flip & 0.4481 & 0.5661 & 0.4334 & 0.5092 \\ \cline{2-6}
-& PRPP & 0.5003 & 0.6115 & 0.3848 & 0.4880 \\ \hline\hline
-\multirow{4}{*}{wt10g} & QC & 0.2873 & 0.3636 & 0.2271* & 0.3436 \\ \cline{2-6}
-& QF & 0.3758 & 0.3847 & 0.3937 & 0.3613 \\ \cline{2-6}
-& PRPP-flip & 0.2758* & 0.4665 & 0.0957* & 0.3949 \\ \cline{2-6}
-& PRPP & 0.2533* & 0.4615 & -0.0181* & 0.4173 \\ \hline\hline
-\multirow{4}{*}{Robust} & QC & 0.4534 & 0.5114 & 0.3768 & 0.3914 \\ \cline{2-6}
-& QF & 0.5061 & 0.5073 & 0.4884 & 0.4926 \\ \cline{2-6}
-& PRPP-flip & 0.5581 & 0.5743 & 0.4889 & 0.5094 \\ \cline{2-6}
-& PRPP & 0.5602 & 0.5791 & 0.4986 & 0.5047 \\ \hline
+\multirow{3}{*}{AP} & QC & 0.3933 & 0.5742 & 0.1858 & 0.3487 \\ \cline{2-6}
+& QF & 0.3561 & 0.5637 & 0.2386 & 0.4467 \\ \cline{2-6}
+%& PRPP-flip & 0.3518 & 0.5661 & \textbf{0.2805} & \textbf{0.5092} \\ \cline{2-6}
+& PRPP & \textbf{0.4152}$^{cf}$ & \textbf{0.6115} & \textbf{0.2513}$^{c}$ & \textbf{0.4880} \\ \hline\hline
+\multirow{3}{*}{wt10g} & QC & 0.1054 & 0.2226 & 0.0027 & 0.0674* \\ \cline{2-6}
+& QF & 0.2220 & 0.3847 & 0.1775 & 0.3613 \\ \cline{2-6}
+%& PRPP-flip & 0.2687 & \textbf{0.4665} & 0.1961 & 0.3949 \\ \cline{2-6}
+& PRPP & \textbf{0.2912}$^{cf}$ & \textbf{0.4615} & \textbf{0.1965}$^{c}$ & \textbf{0.4173} \\ \hline\hline
+\multirow{3}{*}{Robust} & QC & 0.2942 & 0.4284 & 0.2292 & 0.3165 \\ \cline{2-6}
+& QF & 0.3544 & 0.5073 & \textbf{0.3347} & 0.4926 \\ \cline{2-6}
+%& PRPP-flip & 0.3973 & 0.5743 & \textbf{0.3410} & \textbf{0.5094} \\ \cline{2-6}
+& PRPP & \textbf{0.3985}$^{cf}$ & \textbf{0.5791} & 0.3297$^{c}$ & \textbf{0.5047} \\ \hline
 \end{tabular}
-\caption{Median and maximum Pearson's $r$ correlation of predictors for each collection. Bolded values are the largest observed per corpus/metric summary.}
+\caption{Cross-validated and maximum Pearson's $r$ correlation of predictors for each collection.
+$^c$ and $^f$ indicate statistically significant improvement at $p < 0.05$ over query clarity and query feedback respectively.
+Bolded values are the largest observed per corpus/metric summary.
+All correlations are statistically significant unless marked with an asterisk (*).}
 \label{table.results.self.pearson}
@@
 \begin{table}
-\begin{tabular}{|l|l|c|c|c|c|} \hline
+\begin{tabular}{|l|l|l|l|l|l|} \hline
 & & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{3-6}
-Corpus & Pred. & Med. & Max & Med. & Max \\ \hline\hline
-\multirow{4}{*}{AP} & QC & & & & \\ \cline{2-6}
-& QF & & & & \\ \cline{2-6}
-& PRPP-flip & & & & \\ \cline{2-6}
-& PRPP & & & & \\ \hline\hline
-\multirow{4}{*}{wt10g} & QC & & & & \\ \cline{2-6}
-& QF & & & & \\ \cline{2-6}
-& PRPP-flip & & & & \\ \cline{2-6}
-& PRPP & & & & \\ \hline\hline
-\multirow{4}{*}{Robust} & QC & & & & \\ \cline{2-6}
-& QF & & & & \\ \cline{2-6}
-& PRPP-flip & & & & \\ \cline{2-6}
-& PRPP & & & & \\ \hline
+Corpus & Pred. & Valid. & Max. & Valid. & Max. \\ \hline\hline
+\multirow{3}{*}{AP} & QC & 0.3965 & 0.4157 & 0.1997 & 0.2276 \\ \cline{2-6}
+& QF & 0.3601 & 0.4215 & 0.2381 & 0.3010 \\ \cline{2-6}
+%& PRPP-flip & 0.4129 & 0.4670 & \textbf{0.2757} & \textbf{0.3543} \\ \cline{2-6}
+& PRPP & \textbf{0.4554}$^{cf}$ & \textbf{0.4962} & \textbf{0.2521}$^{c}$ & \textbf{0.3378} \\ \hline\hline
+\multirow{3}{*}{wt10g} & QC & 0.0779 & 0.1221* & -0.0017 & 0.0262*\\ \cline{2-6}
+& QF & 0.2088 & 0.2843 & 0.1529 & 0.2411 \\ \cline{2-6}
+%& PRPP-flip & \textbf{0.3020} & \textbf{0.3772} & 0.1960 & 0.2844\\ \cline{2-6}
+& PRPP & \textbf{0.2734}$^{cf}$ & \textbf{0.3642} & \textbf{0.2207}$^{cf}$ & \textbf{0.3053} \\ \hline\hline
+\multirow{3}{*}{Robust} & QC & 0.3070 & 0.3159 & 0.2357 & 0.2418 \\ \cline{2-6}
+& QF & 0.3508 & 0.3745 & 0.3347 & \textbf{0.3646} \\ \cline{2-6}
+%& PRPP-flip & 0.4029 & 0.4148 & 0.3410 & \textbf{0.3698} \\ \cline{2-6}
+& PRPP & \textbf{0.4129}$^{cf}$ & \textbf{0.4273} & \textbf{0.3442}$^{cf}$ & 0.3634 \\ \hline
 \end{tabular}
-\caption{Median and maximum Kendall's $\tau$ correlation of predictors for each collection. Bolded values are the largest observed per corpus/metric summary.}
+\caption{Cross-validated and maximum Kendall's $\tau$ correlation of predictors for each collection.
+$^c$ and $^f$ indicate statistically significant improvement at $p < 0.05$ over query clarity and query feedback respectively.
+Bolded values are the largest observed per corpus/metric summary.
+All correlations are statistically significant unless marked with an asterisk (*).}
 \label{table.results.self.kendall}
@@
 
-The results of our predictor as well as the two baselines are shown in Tables \ref{table.results.self.pearson} and \ref{table.results.self.kendall}; the former displays Pearson's $r$ correlation while the latter displays Kendall's $\tau$ rank correlation.
+The results of our predictor as well as the two baselines are shown in Tables \ref{table.results.self.pearson} and \ref{table.results.self.kendall}; the former displays Pearson's $r$ correlation with the target metric (MAP or nDCG@20) while the latter displays Kendall's $\tau$ rank correlation.
 
-\section{Conclusions}\label{section.conclusions}
+We report the average of the cross-validated runs in the "Valid." column.
+Values marked with superscripts indicate statistically significant improvement over baselines at $p < 0.05$ using a one-tailed paired t-test.
+The tables show that PRPP outperforms the baselines whenever MAP is the target metric; it also outperforms QC with nDCG@20 as the target metric in all cases and outperforms QF for wt10g and robust with Kendall's $\tau$ correlation.
+
+We also report the maximum correlation value seen across all parameter settings.
+This is an oracle metric in that it uses the full set of queries and therefore the full set of relevance judgments.
+As can be seen in Tables \ref{table.results.self.pearson} and \ref{tbale.results.self.kendall}, the maximum prediction accuracy of PRPP is usually the highest across predictors and is often much higher than either baseline.
+The maximum value is included because it is suggestive of the potential of each predictor.
+
+\subsection{Using External Corpora for Prediction}\label{section.results.external}
+
+\begin{table}
+\begin{tabular}{|l|l|l|l|l|l|} \hline
+& & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{3-6}
+Corpus & Pred. & Valid. & Max. & Valid. & Max. \\ \hline\hline
+\multirow{2}{*}{AP} & QC-wiki & 0.1938$^{\downarrow}$ & & 0.0873$^{\downarrow}$ & \\ \cline{2-6}
+& PRPP-wiki & 0.4495$^{\uparrow}$ & & 0.3593$^{\uparrow}$ & \\ \hline\hline
+\multirow{2}{*}{wt10g} & QC-wiki & 0.1496$^{\uparrow}$ & & 0.0996$^{\uparrow}$ & \\ \cline{2-6}
+& PRPP-wiki & 0.3344$^{\uparrow}$ & & 0.2851$^{\uparrow}$ & \\ \hline\hline
+\multirow{2}{*}{Robust} & QC-wiki & 0.2359$^{\downarrow}$ & & 0.2078$^{\downarrow}$ & \\ \cline{2-6}
+& PRPP-wiki & 0.3778$^{\downarrow}$ & & 0.2984$^{\downarrow}$ & \\ \hline
+\end{tabular}
+\caption{}
+\label{table.results.wiki.pearson}
+\end{table}
+
+\begin{table}
+\begin{tabular}{|l|l|l|l|l|l|} \hline
+& & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{3-6}
+Corpus & Pred. & Valid. & Max. & Valid. & Max. \\ \hline\hline
+\multirow{2}{*}{AP} & QC-wiki & 0.1872$^{\downarrow}$ & & 0.0924$^{\downarrow}$ & \\ \cline{2-6}
+& PRPP-wiki & 0.4693$^{\uparrow}$ & & 0.3589$^{\uparrow}$ & \\ \hline\hline
+\multirow{2}{*}{wt10g} & QC-wiki & 0.1538$^{\uparrow}$ & & 0.1028$^{\uparrow}$ & \\ \cline{2-6}
+& PRPP-wiki & 0.3272$^{\uparrow}$ & & 0.2845$^{\uparrow}$ & \\ \hline\hline
+\multirow{2}{*}{Robust} & QC-wiki & 0.2295$^{\downarrow}$ & & 0.2001$^{\downarrow}$ & \\ \cline{2-6}
+& PRPP-wiki & 0.3693$^{\downarrow}$ & & 0.3040$^{\downarrow}$ & \\ \hline
+\end{tabular}
+\caption{}
+\label{table.results.wiki.kendall}
+\end{table}
+
+\section{Discussion \& Conclusions}\label{section.conclusions}
 

### 2017-02-28 expansion/paper.tex
final edits, submitting

@@
 
-\title{Relevance Modeling with Documents Expanded Using External Collections}
+\title{Document Expansion Using External Collections}
 
@@
 That is, there is no guarantee that $D$ is a representative sample from $R$.
-The quality of our RM, therefore, may benefit from a higher quality document representation than that which is available in the collection.
+The quality of our RM, therefore, may benefit from a higher quality document representation than that which is estimated from the text of $D$.
 
@@
 Relevance models are most efficient and robust when calculated over only the top ranked documents and limited to the top terms.
-These parameters are referred to as $fbDocs$ and $fbTerms$ respectively in Table \ref{table.parameters}.
+These parameters are referred to as $fbDocs$ and $fbTerms$ respectively in Table \ref{table.parameters} below.
 
@@
 \ref{eq.ql-and-expansion-mult} allows for an arbitrary number of collections, for now we limit ourselves to two: the collection that the document appears in (the ``target'' collection) and Wikipedia\footnote{http://en.wikipedia.org}.
-The latter, as a general encyclopedia, is hypothesized to yield relatively unbiased probability estimates.
+We expect the latter, as a general encyclopedia, to yield relatively unbiased probability estimates.
 We build an Indri\footnote{http://www.lemurproject.org/indri/} index over the Wikipedia page text.

### 2017-03-01 qpp/paper.tex
final edits, submitting qpp

@@
 \begin{abstract}
+Techniques for estimating the effectiveness of an information retrieval system in the absence of relevance judgments, known as query performance prediction (QPP), generally work by associating some property of a query or its document result set with an evaluation metric like mean average precision.
+We propose a method of QPP that directly incorporates notions of relevance into the prediction process.
+To do this, we rely on the well-known information retrieval technique of pseudo-relevance feedback to approximate relevance judgments and to reformulate the query.
+Our experiments indicate that this approach is very effective at predicting query performance.
 \end{abstract}
@@
 
-Query performance prediction (QPP) is the task of estimating the success of an information retrieval (IR) system in retrieving results for a submitted query.
+Query performance prediction (QPP) is the task of estimating, without reference to relevance judgments, the success of an information retrieval (IR) system in retrieving results for a submitted query.
 Prediction strategies generally use properties of the query or of the retrieved document set to quantify the success of a system.
@@
 In this work, we propose a predictor inspired by pseudo-relevance feedback techniques that directly incorporates relevance metrics in the prediction process.
-We accomplish this by asserting that the top $r$ retreived documents in a ranked list for a query $Q$ are relevant to that query; we then use these pseudo-relevance judgments to estimate document retrieval evaluation using natural variations on the query: the top $n$ ranked documents.
+We accomplish this by asserting that the top retreived documents in a ranked list for a query are relevant to that query; we then use these pseudo-relevance judgments to estimate document retrieval evaluation using natural variations on the query derived from the top ranked documents.
 
@@
 \begin{flalign}\label{eq.clarity}
-\sum_{w \in V} P(w|Q) \log \frac{P(w|Q)}{P(w|C)}
+clarity(Q) = \sum_{w \in V} P(w|Q) \log \frac{P(w|Q)}{P(w|C)}
 \end{flalign}
@@
 
-Zhou \& Croft's query feedback (QF) technique constructs a new query from the top ranked documents \cite{Zhou2007}.
+Zhou \& Croft's query feedback (QF) method is a query perturbation predictor that holds some resemblance to our own \cite{Zhou2007}.
+Their method begins by constructing a new query from the top ranked documents.
 First, QF issues $Q$ against collection $C$, retrieving a results list $L$.
@@
 This overlap is the QF score.
-This technique bears a resemblance to our proposed method: like ours, the top ranked results give rise to alternate queries, and the results lists of the original and alternate queries are compared.
+Like our proposed method, the top ranked results give rise to alternate queries, and the results lists of the original and alternate queries are compared.
 Unlike ours, however, QF produces only a single alternate query; our method also differs in its scoring component, which directly models retrieval performance rather than simply measuring overlap as QF does.
@@
 
-In this paper, we employ the standard multinomial query likelihood (QL) retrieval model to rank the relevance of a document $D$ to query $Q$, although it should be noted that this model is not required by our query performance predictor.
-
+Although our query performance predictor does not require it, in this paper we employ the standard multinomial query likelihood (QL) retrieval model to rank the relevance of a document $D$ to query $Q$.
 Assuming a uniform distribution over documents, QL scores $D$ by the following:
@@
 
-Our query performance predictor, which we call the pseudo-relevance performance predictor (PRPP), is inspired by the pseudo-relevance feedback technique of treating the top ranked documents as relevant to the query.
-Doing so allows us to directly model the robustness of query performance metrics to query perturbation.
-The broad steps of our approach are as follows:
+\begin{figure*}
+%\centering
+\includegraphics[width=\linewidth]{figures/example-queries.pdf}
+\caption{Example pseudo-queries formed in our process.
+Each column displays the top five terms in the pseudo-query and their weights.
+The two original queries appear above ther respective pseudo-queries.}
+\label{figure.queries}
+\end{figure*}
+
+Our query performance predictor, which we call the pseudo-evaluation performance predictor (PEval), is inspired by the pseudo-relevance feedback technique of treating the top ranked documents as relevant to the query.
+Doing so allows us to directly model the robustness of relevance metrics to query perturbation.
+We present the steps involved in our technique, followed by an explanation of key points:
 
 \begin{enumerate}
-	\item Issue query $Q$ against collection $C_p$; call the results list $R_p$
-	\item Record the top $r$ documents in $R_p$ as relevant using each's normalized retrieval score as the degree of relevance
-	\item Issue $Q$ against target collection $C_t$, if $C_p \neq C_t$; call the results list $R_t$
+	\item Issue query $Q$ against performance collection $C_p$; call the results list $R_p$
+	\item Record the top $r$ documents in $R_p$ as relevant using each document's normalized retrieval score as the degree of relevance; all other documents are assumed to be non-relevant
+	\item If $C_p \neq C_t$, issue $Q$ against target collection $C_t$; call the results list $R_t$
 	\item For each document $D$ in $R_t$,
 	\begin{enumerate}
-		\item Construct a pseudo-query $Q_D$ consisting of the top $q$ non-stop terms\footnote{We remove terms in the standard Indri stoplist: http://www.lemurproject.org/stopwords/stoplist.dft} in $D$
-		\item Issue $Q_D$ against $C_p$; call the results list $R_{pD}$
-		\item Score $R_{pD}$ using the pseudo-relevance judgments from Step 2.
+		\item Construct a pseudo-query $Q_D$ consisting of the top $|Q_D|$ non-stop terms\footnote{We remove terms in the standard Indri stoplist: http://www.lemurproject.org/stopwords/stoplist.dft} in $D$
+		\item Issue $Q_D$ against $C_p$; call the results list $R_{Q_D}$
+		\item Score $R_{Q_D}$ for some relevance metric, e.g. average precision, using the pseudo-relevance judgments from Step 2.
 	\end{enumerate}
-	\item Average the scores to compute a single score for $Q$
+	\item Average the scores computed in Step 4 to compute a single score for $Q$
 \end{enumerate}
 
-\noindent Several points in the preceding would benefit from clarification.
+Essentially, our approach emulates an ad-hoc document retrieval evaluation using information from the true, original retrieval: we evaluate the ranked retrieval $R_{Q_D}$ for each query $Q_D$ using relevance judgments $R_p$.
 
-First, our model makes no assertions about the identity of the performance collection $C_p$.
+Our model makes no assertions about the identity of the performance collection $C_p$.
 While it is valid to use the target collection as the performance collection, we hypothesize that the use of an external collection may yield better results.
@@
 
-Next, both $r$ and $q$ are free parameters in our approach.
-In fact, there are two other parameters in our approach: $k$ controls the length of $R_t$, while $n$ controls the length of $R_{pD}$.
+Both $r$ and $|Q_D|$ are free parameters in our approach, as are two additional parameters: $k$ controls the length of $R_t$, while $n$ controls the length of $R_{Q_D}$.
 In general, all parameters should be set empirically.
-Although not required mathematically, we only allow values of $n$ where $n \leq r$ since setting $n$ greater than $r$ prevents us from retrieving all relevant documents.
+Although not required mathematically, we only allow values of $n$ where $n \leq r$ since setting $n$ greater than $r$ prevents us from achieving perfect recall, i.e.
+from retrieving all pseudo-relevant documents.
 
 One advantage to our model is the ability to predict specific retrieval metrics by estimating levels of relevance.
-Because these levels are normalized log probabilities, they consist of continuous values (in contrast to TREC qrels which contain binary or discrete relevance grades), but are still valid for metrics that incorporate graded relevance judgments like normalized discounted cumulative gain (nDCG).
-Metrics that use only binary relevance metrics, like mean average precision (MAP) follow the typical procedure of treating all judgments greater than zero as relevant.
+As Step 2 states, we estimate levels of relevance by normalizing the retrieval scores of the documents in $R_p$.
+This follows from the pseudo-relevance feedback technique of treating top ranked documents as relevant by simply treating \textit{more highly} ranked documents as \textit{more relevant}.
+We use the normalized retrieval scores rather than the rankings themselves in order to allow documents to achieve similar levels of relevance if their scores are similar.
+
+Because these relevance levels are normalized probabilities, they consist of continuous values (in contrast to TREC qrels which contain binary or discrete relevance grades), but are still valid for metrics that incorporate graded relevance judgments like normalized discounted cumulative gain (nDCG).
+Metrics that use only binary relevance metrics, like mean average precision (MAP), follow the typical procedure of treating all judgments greater than zero as relevant.
 
@@
 
-We also make use of Wikipedia\footnote{http://en.wikipedia.org} as an external collection in some experiments.
+We also make use of an indexed dump of Wikipedia\footnote{http://en.wikipedia.org} as an external collection in some experiments.
 
@@
 Our predictor requires the setting of several parameters.
-We set $r$, $k$, and $n$ by cross-validation: we sweep over each parameter at the values $\{1, 5, 10, 20, 50, 75, 100\}$; as noted in Section \ref{section.method}, $n$ is only swept at values $\leq r$.
-We fix $q = 20$ for all runs since using the entire length of $D$, $|D|$, is excessively expensive during retrieval.
+We set $r$, $k$, and $n$ by cross-validation: we sweep over each parameter at the values $\{1, 5, 10, 20, 50, 75, 100\}$.
+As noted in Section \ref{section.method}, $n$ is only swept at values $\leq r$.
+We fix $|Q_D| = 20$ for all runs since using the entire length of $D$, $|D|$, is excessively expensive during retrieval.
 
@@
 We choose an equal split over other forms of cross-validation in order to provide a relatively large number of queries to each fold, leading to more stable correlation values.
-We repeat this procedure 100 times, splitting the query set randomly each time, and average the correlation values to compute an average query performance prediction.
+We repeat this procedure 100 times, splitting the query set randomly each time, and average the correlation values to compute an average query performance prediction score.
 
@@
 
-% \begin{table}
-% \begin{tabular}{|l|l|c|c|c|c|} \hline
-% & & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{3-6}
-% Corpus & Pred. & Med. & Max & Med. & Max \\ \hline\hline
-% \multirow{4}{*}{AP} & QC & \textbf{0.5280} & \textbf{0.6148} & 0.3564 & 0.4284 \\ \cline{2-6}
-% & QF & 0.4240 & 0.5637 & 0.3202 & 0.4467 \\ \cline{2-6}
-% & PRPP-flip & 0.5020 & 0.5661 & \textbf{0.4026} & \textbf{0.5092} \\ \cline{2-6}
-% & PRPP & 0.5030 & 0.6115 & 0.4025 & 0.4880 \\ \hline\hline
-% \multirow{4}{*}{wt10g} & QC & 0.2232 & 0.3636 & 0.0943 & 0.3436 \\ \cline{2-6}
-% & QF & 0.1624 & 0.3847 & 0.0881 & 0.3613 \\ \cline{2-6}
-% & PRPP-flip & 0.2910 & 0.4665 & 0.2367 & 0.3949 \\ \cline{2-6}
-% & PRPP & \textbf{0.2850} & \textbf{0.4615} & \textbf{0.2529} & \textbf{0.4173} \\ \hline\hline
-% \multirow{4}{*}{Robust} & QC & 0.4240 & 0.5114 & 0.3129 & 0.3914 \\ \cline{2-6}
-% & QF & 0.2203 & 0.5073 & 0.1708 & 0.4926 \\ \cline{2-6}
-% & PRPP-flip & 0.3826 & 0.5743 & 0.3540 & 0.5094 \\ \cline{2-6}
-% & PRPP & \textbf{0.4381} & \textbf{0.5791} & \textbf{0.3222} & \textbf{0.5047} \\ \hline
-% \end{tabular}
-% \caption{Median and maximum Pearson's $r$ correlation of predictors for each collection. Bolded values are the largest observed per corpus/metric summary.}
-% \label{table.results.self.pearson}
-% \end{table}
-% 
-% \begin{table}
-% \begin{tabular}{|l|l|c|c|c|c|} \hline
-% & & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{3-6}
-% Corpus & Pred. & Med. & Max & Med. & Max \\ \hline\hline
-% \multirow{4}{*}{AP} & QC & 0.3609 & 0.4440 & 0.2166 & 0.2807 \\ \cline{2-6}
-% & QF & 0.3259 & 0.4215 & 0.2042 & 0.3100 \\ \cline{2-6}
-% & PRPP-flip & 0.4068 & 0.4670 & \textbf{0.2769} & \textbf{0.3543} \\ \cline{2-6}
-% & PRPP & \textbf{0.4132} & \textbf{0.4962} & 0.2701 & 0.3378 \\ \hline\hline
-% \multirow{4}{*}{wt10g} & QC & 0.1561 & 0.3093 & 0.0712 & 0.2622 \\ \cline{2-6}
-% & QF & 0.1599 & 0.2843 & 0.0657 & 0.2411 \\ \cline{2-6}
-% & PRPP-flip & 0.2586 & 0.3772 & 0.2006 & 0.2844 \\ \cline{2-6}
-% & PRPP & \textbf{0.2710} & \textbf{0.3642} & \textbf{0.1935} & \textbf{0.3053} \\ \hline\hline
-% \multirow{4}{*}{Robust} & QC & 0.2985 & 0.3714 & 0.2266 & 0.2889 \\ \cline{2-6}
-% & QF & 0.1895 & 0.3745 & 0.1389 & \textbf{0.3646} \\ \cline{2-6}
-% & PRPP-flip & 0.3082 & 0.4148 & 0.2783 & 0.3698 \\ \cline{2-6}
-% & PRPP & \textbf{0.3433} & \textbf{0.4273} & \textbf{0.2478} & 0.3634 \\ \hline
-% \end{tabular}
-% \caption{Median and maximum Kendall's $\tau$ correlation of predictors for each collection. Bolded values are the largest observed per corpus/metric summary.}
-% \label{table.results.self.kendall}
-% \end{table}
-
-% \begin{table}
-% \begin{tabular}{|l|l|c|c|c|c|} \hline
-% & & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{3-6}
-% Corpus & Pred. & Valid. & Max. & Valid. & Max \\ \hline\hline
-% \multirow{4}{*}{AP} & QC & 0.4748 & 0.6148 & 0.2488* & 0.4284 \\ \cline{2-6}
-% & QF & 0.5178 & 0.5637 & 0.2368* & 0.4467 \\ \cline{2-6}
-% & PRPP-flip & 0.4481 & 0.5661 & 0.4334 & 0.5092 \\ \cline{2-6}
-% & PRPP & 0.5003 & 0.6115 & 0.3848 & 0.4880 \\ \hline\hline
-% \multirow{4}{*}{wt10g} & QC & 0.2873 & 0.3636 & 0.2271* & 0.3436 \\ \cline{2-6}
-% & QF & 0.3758 & 0.3847 & 0.3937 & 0.3613 \\ \cline{2-6}
-% & PRPP-flip & 0.2758* & 0.4665 & 0.0957* & 0.3949 \\ \cline{2-6}
-% & PRPP & 0.2533* & 0.4615 & -0.0181* & 0.4173 \\ \hline\hline
-% \multirow{4}{*}{Robust} & QC & 0.4534 & 0.5114 & 0.3768 & 0.3914 \\ \cline{2-6}
-% & QF & 0.5061 & 0.5073 & 0.4884 & 0.4926 \\ \cline{2-6}
-% & PRPP-flip & 0.5581 & 0.5743 & 0.4889 & 0.5094 \\ \cline{2-6}
-% & PRPP & 0.5602 & 0.5791 & 0.4986 & 0.5047 \\ \hline
-% \end{tabular}
-% \caption{Median and maximum Pearson's $r$ correlation of predictors for each collection. Bolded values are the largest observed per corpus/metric summary.}
-% \label{table.results.self.pearson}
-% \end{table}
-
-\begin{table}
+\begin{table}[t]
+\centering
 \begin{tabular}{|l|l|l|l|l|l|} \hline
 & & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{3-6}
-Corpus & Pred. & Valid. & Max. & Valid. & Max \\ \hline\hline
+Corpus & Run & Valid. & Max. & Valid. & Max \\ \hline\hline
 \multirow{3}{*}{AP} & QC & 0.3933 & 0.5742 & 0.1858 & 0.3487 \\ \cline{2-6}
 & QF & 0.3561 & 0.5637 & 0.2386 & 0.4467 \\ \cline{2-6}
-%& PRPP-flip & 0.3518 & 0.5661 & \textbf{0.2805} & \textbf{0.5092} \\ \cline{2-6}
-& PRPP & \textbf{0.4152}$^{cf}$ & \textbf{0.6115} & \textbf{0.2513}$^{c}$ & \textbf{0.4880} \\ \hline\hline
+%& PEval-flip & 0.3518 & 0.5661 & \textbf{0.2805} & \textbf{0.5092} \\ \cline{2-6}
+& PEval & \textbf{0.4152}$^{cf}$ & \textbf{0.6115} & \textbf{0.2513}$^{c}$ & \textbf{0.4880} \\ \hline\hline
 \multirow{3}{*}{wt10g} & QC & 0.1054 & 0.2226 & 0.0027 & 0.0674* \\ \cline{2-6}
 & QF & 0.2220 & 0.3847 & 0.1775 & 0.3613 \\ \cline{2-6}
-%& PRPP-flip & 0.2687 & \textbf{0.4665} & 0.1961 & 0.3949 \\ \cline{2-6}
-& PRPP & \textbf{0.2912}$^{cf}$ & \textbf{0.4615} & \textbf{0.1965}$^{c}$ & \textbf{0.4173} \\ \hline\hline
+%& PEval-flip & 0.2687 & \textbf{0.4665} & 0.1961 & 0.3949 \\ \cline{2-6}
+& PEval & \textbf{0.2912}$^{cf}$ & \textbf{0.4615} & \textbf{0.1965}$^{c}$ & \textbf{0.4173} \\ \hline\hline
 \multirow{3}{*}{Robust} & QC & 0.2942 & 0.4284 & 0.2292 & 0.3165 \\ \cline{2-6}
 & QF & 0.3544 & 0.5073 & \textbf{0.3347} & 0.4926 \\ \cline{2-6}
-%& PRPP-flip & 0.3973 & 0.5743 & \textbf{0.3410} & \textbf{0.5094} \\ \cline{2-6}
-& PRPP & \textbf{0.3985}$^{cf}$ & \textbf{0.5791} & 0.3297$^{c}$ & \textbf{0.5047} \\ \hline
+%& PEval-flip & 0.3973 & 0.5743 & \textbf{0.3410} & \textbf{0.5094} \\ \cline{2-6}
+& PEval & \textbf{0.3985}$^{cf}$ & \textbf{0.5791} & 0.3297$^{c}$ & \textbf{0.5047} \\ \hline
 \end{tabular}
@@
 
-\begin{table}
+\begin{table}[t]
+\centering
 \begin{tabular}{|l|l|l|l|l|l|} \hline
 & & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{3-6}
-Corpus & Pred. & Valid. & Max. & Valid. & Max. \\ \hline\hline
+Corpus & Run & Valid. & Max. & Valid. & Max. \\ \hline\hline
 \multirow{3}{*}{AP} & QC & 0.3965 & 0.4157 & 0.1997 & 0.2276 \\ \cline{2-6}
 & QF & 0.3601 & 0.4215 & 0.2381 & 0.3010 \\ \cline{2-6}
-%& PRPP-flip & 0.4129 & 0.4670 & \textbf{0.2757} & \textbf{0.3543} \\ \cline{2-6}
-& PRPP & \textbf{0.4554}$^{cf}$ & \textbf{0.4962} & \textbf{0.2521}$^{c}$ & \textbf{0.3378} \\ \hline\hline
+%& PEval-flip & 0.4129 & 0.4670 & \textbf{0.2757} & \textbf{0.3543} \\ \cline{2-6}
+& PEval & \textbf{0.4554}$^{cf}$ & \textbf{0.4962} & \textbf{0.2521}$^{c}$ & \textbf{0.3378} \\ \hline\hline
 \multirow{3}{*}{wt10g} & QC & 0.0779 & 0.1221* & -0.0017 & 0.0262*\\ \cline{2-6}
 & QF & 0.2088 & 0.2843 & 0.1529 & 0.2411 \\ \cline{2-6}
-%& PRPP-flip & \textbf{0.3020} & \textbf{0.3772} & 0.1960 & 0.2844\\ \cline{2-6}
-& PRPP & \textbf{0.2734}$^{cf}$ & \textbf{0.3642} & \textbf{0.2207}$^{cf}$ & \textbf{0.3053} \\ \hline\hline
+%& PEval-flip & \textbf{0.3020} & \textbf{0.3772} & 0.1960 & 0.2844\\ \cline{2-6}
+& PEval & \textbf{0.2734}$^{cf}$ & \textbf{0.3642} & \textbf{0.2207}$^{cf}$ & \textbf{0.3053} \\ \hline\hline
 \multirow{3}{*}{Robust} & QC & 0.3070 & 0.3159 & 0.2357 & 0.2418 \\ \cline{2-6}
 & QF & 0.3508 & 0.3745 & 0.3347 & \textbf{0.3646} \\ \cline{2-6}
-%& PRPP-flip & 0.4029 & 0.4148 & 0.3410 & \textbf{0.3698} \\ \cline{2-6}
-& PRPP & \textbf{0.4129}$^{cf}$ & \textbf{0.4273} & \textbf{0.3442}$^{cf}$ & 0.3634 \\ \hline
+%& PEval-flip & 0.4029 & 0.4148 & 0.3410 & \textbf{0.3698} \\ \cline{2-6}
+& PEval & \textbf{0.4129}$^{cf}$ & \textbf{0.4273} & \textbf{0.3442}$^{cf}$ & 0.3634 \\ \hline
 \end{tabular}
@@
 
+A few sample pseudo-queries are shown in Figure \ref{figure.queries} along with the original query that they are meant to approximate.
+We can see that in general the pseudo-queries tend to stay related to the topic expressed in the original query; in some cases, however, such as the final pseudo-query shown for the original robust query, a great deal of noise can be introduced.
+This type of noise arises naturally from the language of the retrieved documents.
+
 The results of our predictor as well as the two baselines are shown in Tables \ref{table.results.self.pearson} and \ref{table.results.self.kendall}; the former displays Pearson's $r$ correlation with the target metric (MAP or nDCG@20) while the latter displays Kendall's $\tau$ rank correlation.
@@
 Values marked with superscripts indicate statistically significant improvement over baselines at $p < 0.05$ using a one-tailed paired t-test.
-The tables show that PRPP outperforms the baselines whenever MAP is the target metric; it also outperforms QC with nDCG@20 as the target metric in all cases and outperforms QF for wt10g and robust with Kendall's $\tau$ correlation.
+The tables show that PEval outperforms the baselines whenever MAP is the target metric; it also outperforms QC with nDCG@20 as the target metric in all cases and outperforms QF for wt10g and robust with Kendall's $\tau$ correlation.
 
@@
 This is an oracle metric in that it uses the full set of queries and therefore the full set of relevance judgments.
-As can be seen in Tables \ref{table.results.self.pearson} and \ref{tbale.results.self.kendall}, the maximum prediction accuracy of PRPP is usually the highest across predictors and is often much higher than either baseline.
+As can be seen in Tables \ref{table.results.self.pearson} and \ref{table.results.self.kendall}, the maximum prediction accuracy of PEval is usually the highest across predictors and is often much higher than either baseline.
 The maximum value is included because it is suggestive of the potential of each predictor.
@@
 \begin{table}
+\centering
 \begin{tabular}{|l|l|l|l|l|l|} \hline
-& & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{3-6}
-Corpus & Pred. & Valid. & Max. & Valid. & Max. \\ \hline\hline
-\multirow{2}{*}{AP} & QC-wiki & 0.1938$^{\downarrow}$ & & 0.0873$^{\downarrow}$ & \\ \cline{2-6}
-& PRPP-wiki & 0.4495$^{\uparrow}$ & & 0.3593$^{\uparrow}$ & \\ \hline\hline
-\multirow{2}{*}{wt10g} & QC-wiki & 0.1496$^{\uparrow}$ & & 0.0996$^{\uparrow}$ & \\ \cline{2-6}
-& PRPP-wiki & 0.3344$^{\uparrow}$ & & 0.2851$^{\uparrow}$ & \\ \hline\hline
-\multirow{2}{*}{Robust} & QC-wiki & 0.2359$^{\downarrow}$ & & 0.2078$^{\downarrow}$ & \\ \cline{2-6}
-& PRPP-wiki & 0.3778$^{\downarrow}$ & & 0.2984$^{\downarrow}$ & \\ \hline
+& \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{2-5}
+Corpus & Valid. & Max. & Valid. & Max. \\ \hline\hline
+% \multirow{2}{*}{AP} & QC$_w$ & 0.1938$^{\downarrow}$ & & 0.0873$^{\downarrow}$ & \\ \hline
+AP & \textbf{0.4495}$^{\uparrow}$ & \textbf{0.6740} & \textbf{0.3593}$^{\uparrow}$ & \textbf{0.5742} \\ \hline
+% \multirow{2}{*}{wt10g} & QC$_w$ & 0.1496$^{\uparrow}$ & & 0.0996$^{\uparrow}$ & \\ \hline
+wt10g & \textbf{0.3344}$^{\uparrow}$ & \textbf{0.5487} & \textbf{0.2851}$^{\uparrow}$ & \textbf{0.5163} \\ \hline
+% \multirow{2}{*}{Robust} & QC$_w$ & 0.2359$^{\downarrow}$ & & 0.2078$^{\downarrow}$ & \\ \hline
+Robust & 0.3778$^{\downarrow}$ & 0.4821 & 0.2984$^{\downarrow}$ & 0.4333 \\ \hline
 \end{tabular}
-\caption{}
+\caption{Pearson's $r$ correlation for PEval using Wikipedia as the performance collection.
+$\uparrow$ and $\downarrow$ indicate statistically significant ($p < 0.05$) improvement and decline, respectively, relative to the corresponding run in Table \ref{table.results.self.pearson}.
+Bolded values are greater than than the corresponding value in Table \ref{table.results.self.pearson}.}
 \label{table.results.wiki.pearson}
@@
 \begin{table}
+\centering
 \begin{tabular}{|l|l|l|l|l|l|} \hline
-& & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{3-6}
-Corpus & Pred. & Valid. & Max. & Valid. & Max. \\ \hline\hline
-\multirow{2}{*}{AP} & QC-wiki & 0.1872$^{\downarrow}$ & & 0.0924$^{\downarrow}$ & \\ \cline{2-6}
-& PRPP-wiki & 0.4693$^{\uparrow}$ & & 0.3589$^{\uparrow}$ & \\ \hline\hline
-\multirow{2}{*}{wt10g} & QC-wiki & 0.1538$^{\uparrow}$ & & 0.1028$^{\uparrow}$ & \\ \cline{2-6}
-& PRPP-wiki & 0.3272$^{\uparrow}$ & & 0.2845$^{\uparrow}$ & \\ \hline\hline
-\multirow{2}{*}{Robust} & QC-wiki & 0.2295$^{\downarrow}$ & & 0.2001$^{\downarrow}$ & \\ \cline{2-6}
-& PRPP-wiki & 0.3693$^{\downarrow}$ & & 0.3040$^{\downarrow}$ & \\ \hline
+& \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{2-5}
+Corpus & Valid. & Max. & Valid. & Max. \\ \hline\hline
+% \multirow{2}{*}{AP} & QC$_w$ & 0.1872$^{\downarrow}$ & & 0.0924$^{\downarrow}$ & \\ \hline
+AP & \textbf{0.4693}$^{\uparrow}$ & \textbf{0.5082} & \textbf{0.3589}$^{\uparrow}$ & \textbf{0.4170} \\ \hline
+% \multirow{2}{*}{wt10g} & QC$_w$ & 0.1538$^{\uparrow}$ & & 0.1028$^{\uparrow}$ & \\ \hline
+wt10g & \textbf{0.3272}$^{\uparrow}$ & \textbf{0.4131} & \textbf{0.2845}$^{\uparrow}$ & \textbf{0.3781} \\ \hline
+% \multirow{2}{*}{Robust} & QC$_w$ & 0.2295$^{\downarrow}$ & & 0.2001$^{\downarrow}$ & \\ \hline
+Robust & 0.3693$^{\downarrow}$ & 0.3909 & 0.3040$^{\downarrow}$ & 0.3355 \\ \hline
 \end{tabular}
-\caption{}
+\caption{Kendall's $\tau$ correlation for PEval using Wikipedia as the performance collection.
+$\uparrow$ and $\downarrow$ indicate statistically significant ($p < 0.05$) improvement and decline, respectively, relative to the corresponding run in Table \ref{table.results.self.kendall}.
+Bolded values are greater than than the corresponding value in Table \ref{table.results.self.kendall}.}
 \label{table.results.wiki.kendall}
@@
 
+As mentioned in Section \ref{section.method.predicting}, PEval does not require that the performance collection and target collection be the same.
+One intuitive reason an external collection may be beneficial is if the top ranked documents $R_t$ are not representative of the true relevant documents in the collection; in this case, we would expect PEval to overpredict performance since the evaluation of the pseudo-queries based on $R_t$ is likely to mask the original query's failure to match dissimilar relevant documents.
+In contrast, if $R_p$ were derived from an external collection, we reduce the chance that the pseudo-relevant documents will exhibit the same bias that may affect $R_t$, thus improving our prediction.
+
+%To understand the intuition behind using an external performance collection, consider an extreme case in which some form of collection bias causes the top ranked documents $R_t$ for query $Q$ in collection $C_t$ share \textit{no} vocabulary with the remainder of $C_t$.
+This does not imply that $R_t$ comprises the entirety of the relevant document set for $Q$---there may be relevant documents outside of $R_t$ that simply suffer from complete vocabulary mismatch---nor does it imply that all documents in $R_t$ are relevant.
+If we use $C_t$ as the performance collection $C_p$, we are likely to overestimate the query performance because the pseudo-relevant documents will consistently rank one another highly when issued as pseudo-queries.
+
+%If, on the other hand, we use an external collection as $C_p$, we reduce the chance that the pseudo-relevant documents will exhibit the same vocabulary bias that may affect the top ranked documents in $C_t$, thus improving our estimation of the effects of query perturbation and improving our predictor's performance.
+
+We use Wikipedia to test whether our intuition about using external collections is true.
+These results are reported in Tables \ref{table.results.wiki.pearson} and \ref{table.results.wiki.kendall}.
+Both AP and wt10g improve significantly over their non-external counterparts in Tables \ref{table.results.self.pearson} and \ref{table.results.self.kendall} with statistical significance at $p < 0.05$.
+Unfortunately, robust performs in the opposite manner, declining in performance with statistical significance.
+
+After analyzing the three collections, it remains unclear why robust is damaged by the use of an external collection.
+However, we are reassured that the lowest absolute differences between PEval results with and without the expansion collection are seen in robust in all but one case.
+In other words, although the effects of using an expansion collection are statistically significant in all cases, the \textit{magnitude} of the effects is greatest when the expansion collection improves performance.
+
 \section{Discussion \& Conclusions}\label{section.conclusions}
+
+We have presented a novel technique for query performance prediction called pseudo-relevance performance prediction, which is inspired by pseudo-relevance feedback.
+As in pseudo-relevance feedback, our predictor assumes that the top documents returned for a query are relevant to that query.
+We then transform top ranked documents into pseudo-queries, which, due to their retrieval rank, we believe are likely to closely represent the query.
+Because the pseudo-queries are noisy approximations of the original query, PEval is essentially a query perturbation method.
+By performing a retrieval for these pseudo-queries and evaluating the results using the pseudo-relevance judgments, we estimate the performance of the original query with true relevance judgments.
+
+Our experiments demonstrate that this method of QPP generally outperforms two typical baselines for both mean average precision and nDCG@20.
+We can increase this performance for two out of three collections by using an external collection to create the pseudo-relevance judgments.
+Although we are concerned about the damage done to robust when using an external collection, we are encouraged by the overall prediction quality of PEval.
+
+Because of its ties to pseudo-relevance feedback, the next logical step for PEval is to investigate its relationship to query expansion.
+In future work, we plan to explore this association and apply our findings to improve ad-hoc document retrieval results.
 

### 2017-04-13 expansion/paper.tex
addressing some comments

@@
-\documentclass{sig-alternate}
+\documentclass[sigconf]{acmart}
 \usepackage{amsmath}
@@
 \usepackage{colortbl}
-\usepackage[table]{xcolor}
+%\usepackage[table]{xcolor}
 
@@
 
-%\author{Garrick Sherman}
-\author{[Blind]}
+\author{Garrick Sherman}
+
+\copyrightyear{2017}
+\acmYear{2017}
+\setcopyright{acmcopyright}
+\acmConference{SIGIR '17}{}{August 7--11, 2017, Shinjuki, Tokyo, Japan}
+\acmPrice{15.00.}
+\acmDOI{http://dx.doi.org/10.1145/XXXXXXX.XXXXXXX}
+\acmISBN{ISBN 978-1-4503-5022-8/17/08}
 
@@
 
-\maketitle
 \begin{abstract}
@@
 \end{abstract}
+
+\maketitle
 
@@
 
-%We can use this idea to expand the query representation into an estimate of the relevance model (see Section \ref{section.expanding.model.rm} for more details) and rank documents by the similarity of their estimated language model to the estimated RM.
+%We can use this idea to expand the query representation into an estimate of the relevance model (see Section~\ref{section.expanding.model.rm} for more details) and rank documents by the similarity of their estimated language model to the estimated RM.
 
@@
 
-Document expansion has been well studied in information retrieval literature, e.g.
-\cite{Liu2004, Singhal1999, Tao2006, Wei2006}.
+Document expansion has been well studied in information retrieval literature, e.g.\ \cite{Liu2004, Singhal1999, Tao2006, Wei2006}.
 For example, Liu \& Croft propose a method of retrieval that uses document clusters to smooth document language models \cite{Liu2004}.
-Tao et al.
-propose a similar approach but place each document at the center of its own cluster; this helps to ensure that the expansion documents are as closely related to the target document as possible \cite{Tao2006}.
+Tao et al.\ propose a similar approach but place each document at the center of its own cluster; this helps to ensure that the expansion documents are as closely related to the target document as possible \cite{Tao2006}.
 
@@
 The incorporation of external collections into document retrieval is a similarly common theme in the ad-hoc IR literature, particularly with respect to query expansion \cite{Bendersky2012, Diaz2006, Li2007, Weerkamp2009, Xu2009}.
-Of particular relevance to our work is that of Diaz \& Metzler, whose mixture of relevance models is the basis of our Eq.
-\ref{eq.ql-and-expansion-mult} \cite{Diaz2006}.
+Of particular relevance to our work is that of Diaz \& Metzler, whose mixture of relevance models is the basis of our Eq.~\ref{eq.ql-and-expansion-mult} \cite{Diaz2006}.
 Their model simply interpolates RMs built on different collections, weighting each by a query-independent quantity $P(c)$.
@@
 \noindent where $c(w, Q)$ is the frequency of word $w$ in $Q$.
-We follow standard procedures for estimating $P(w|\theta_D)$ in Eq.
-\ref{equation.ql}, estimating a smoothed language model by assuming that document language models in a given collection have a Dirichlet prior distribution:
+We follow standard procedures for estimating $P(w|\theta_D)$ in Eq.~\ref{equation.ql}, estimating a smoothed language model by assuming that document language models in a given collection have a Dirichlet prior distribution:
 
@@
 
-\noindent where $P(Q|D)$ is calculated as in Eq.
-\ref{equation.ql} and essentially weights word $w$ in $D$ by the query likelihood of the document.
+\noindent where $P(Q|D)$ is calculated as in Eq.~\ref{equation.ql} and essentially weights word $w$ in $D$ by the query likelihood of the document.
 Relevance models are most efficient and robust when calculated over only the top ranked documents and limited to the top terms.
-These parameters are referred to as $fbDocs$ and $fbTerms$ respectively in Table \ref{table.parameters} below.
+These parameters are referred to as $fbDocs$ and $fbTerms$ respectively in Table~\ref{table.parameters} below.
 
@@
 First we remove all terms from $D$ that appear in the standard Indri stoplist\footnote{http://www.lemurproject.org/stopwords/stoplist.dft}.
-Next, we prune our pseudo-query by retaining only the $0 < k \leq |D|$ most frequent words in the stopped text of $D$.
+Next, we prune our pseudo-query by retaining only the $0 < k \leq K$ most frequent words in the stopped text of $D$, where $K$ is the total number of unique terms in $D$.
 The integer variable $k$ is a parameter that we choose empirically.
+These are the non-stop words with the highest probabilities in a maximum likelihood estimate of $D$'s language model and are therefore a reasonable representation of the topic of the document.
+Though some information may be lost with stopping, with a large enough $k$ we hope to nevertheless capture the general topic of a document; for example, a document about Hamlet's famous speech may not be represented by the terms ``to be or not to be,'' but the terms ``Shakespeare,'' ``Hamlet,'' ``speech,'' etc.
+will likely represent the document's subject sufficiently.
 Let $Q_D$ be the pseudo-query for $D$, consisting of the text of $D$ after our two transformations are applied.
 
-We rank related documents, called expansion documents, by running $Q_D$ over an index $C_E$.
-More formally, we rank the documents in $C_E$ against $D$ using Eq.
-\ref{equation.ql}, substituting $Q_D$ for the query and $E_i$---the $i^{th}$ expansion document---for the document.
-Let $\pi_i$ be the log-probability for expansion document $E_i$ with respect to $D$ given by Eq.
-\ref{equation.ql}.
+We rank related documents, called expansion documents, by running $Q_D$ over a collection $C_E$.
+More formally, we rank the documents in $C_E$ against $D$ using Eq.~\ref{equation.ql}, substituting $Q_D$ for the query and $E_i$---the $i^{th}$ expansion document---for the document.
+Let $\pi_i$ be the log-probability for expansion document $E_i$ with respect to $D$ given by Eq.~\ref{equation.ql}.
 
@@
 Given our motivating intuition that document expansion allows for the more accurate estimation of document language models, we would expect that an RM computed using expanded documents should be more accurate than a standard RM.
-We therefore compute an RM3 as in Eqs.
-\ref{equation.rm1} and \ref{equation.rm3}, substituting the expanded document for the original.
+We therefore compute an RM3 as in Eqs.~\ref{equation.rm1} and~\ref{equation.rm3}, substituting the expanded document for the original.
 
@@
 
-Although Eq.
-\ref{eq.ql-and-expansion-mult} allows for an arbitrary number of collections, for now we limit ourselves to two: the collection that the document appears in (the ``target'' collection) and Wikipedia\footnote{http://en.wikipedia.org}.
+Although Eq.~\ref{eq.ql-and-expansion-mult} allows for an arbitrary number of collections, for now we limit ourselves to two: the collection that the document appears in (the ``target'' collection) and Wikipedia\footnote{http://en.wikipedia.org}.
 We expect the latter, as a general encyclopedia, to yield relatively unbiased probability estimates.
@@
 Stop words are removed from the query.
-For efficiency, we retrieve the top 1000 documents using the default Indri QL implementation and re-rank these documents based on their expanded representations as described in Section \ref{section.model}.
+For efficiency, we retrieve the top 1000 documents using the default Indri QL implementation and re-rank these documents based on their expanded representations as described in Section~\ref{section.model}.
 
@@
 
-The parameters required for our approach, their meanings, and the values used in our experiments are shown in Table \ref{table.parameters}.
+The parameters required for our approach, their meanings, and the values used in our experiments are shown in Table~\ref{table.parameters}.
 
 For this work, we set $k$ heuristically.
-In principle, this parameter need not be limited beyond the length of the document; however, this would increase computation time significantly, so we have set it to a reasonable value.
-The parameter $n$ is also set heuristically; see Section \ref{section.n-sensitivity} for a discussion of the sensitivity of our model to the setting of $n$.
+In principle, $k$ may equal the length of the document; however, this would increase computation time significantly, so we have set it to a smaller value for efficiency.
+The parameter $n$ is also set heuristically; see Section~\ref{section.n-sensitivity} for a discussion of the sensitivity of our model to the setting of $n$.
 
@@
 
-Retrieval effectiveness of each run is shown in Table \ref{table.effectiveness}.
+Retrieval effectiveness of each run is shown in Table~\ref{table.effectiveness}.
 We measure effectiveness with mean average precision (MAP) and normalized discounted cumulative gain at 20 (nDCG@20).
@@
 
-Figure \ref{figure.n-sweeps} shows sweeps over several values of $n$, the number of expansion documents, for the \textit{self} and \textit{wiki} QL runs using our established cross-validation procedure with identical folds.
+Figure~\ref{figure.n-sweeps} shows sweeps over several values of $n$, the number of expansion documents, for the \textit{self} and \textit{wiki} QL runs using our established cross-validation procedure with identical folds.
 The sensitivity to $n$ is not pronounced at $n \geq 5$, and what little variation exists is not consistent across collections.

### 2017-05-16 expansion/paper.tex
addressing comments and fixed float situation

@@
 \documentclass[sigconf]{acmart}
+\usepackage{afterpage}
 \usepackage{amsmath}
@@
 
-\setlist[itemize]{noitemsep}  % remove space between list items
+\setcounter{topnumber}{8}
+\setcounter{bottomnumber}{8}
+\setcounter{totalnumber}{8}
 
@@
 \author{Garrick Sherman}
+\affiliation{School of Information Sciences\\University of Illinois at Urbana-Champaign}
+\email{gsherma2@illinois.edu}
+\author{Miles Efron}
+\affiliation{School of Information Sciences\\University of Illinois at Urbana-Champaign}
+\email{mefron@illinois.edu}
 
@@
 \acmYear{2017}
-\setcopyright{acmcopyright}
-\acmConference{SIGIR '17}{}{August 7--11, 2017, Shinjuki, Tokyo, Japan}
-\acmPrice{15.00.}
-\acmDOI{http://dx.doi.org/10.1145/XXXXXXX.XXXXXXX}
-\acmISBN{ISBN 978-1-4503-5022-8/17/08}
+\setcopyright{acmlicensed}
+\acmConference{SIGIR '17}{August 07-11, 2017}{Shinjuku, Tokyo, Japan}\acmPrice{15.00}\acmDOI{http://dx.doi.org/10.1145/3077136.3080716}
+\acmISBN{978-1-4503-5022-8/17/08}
 
@@
 We expect the latter, as a general encyclopedia, to yield relatively unbiased probability estimates.
-We build an Indri\footnote{http://www.lemurproject.org/indri/} index over the Wikipedia page text.
+We build an Indri \cite{Strohman2005} index over the Wikipedia page text.
 
@@
 \begin{itemize}
-	\item The \textbf{AP} newswire collection from TREC disks 1 and 2 with topics 101-200.
-	\item The \textbf{robust} 2004 topics, numbering 250, from TREC disks 4 and 5.
-	\item The \textbf{wt10g} collection with the 100 topics from the 2000 and 2001 TREC Web tracks.
+	\item The \textbf{AP} newswire collection \cite{Harman1992} from TREC disks 1 and 2 with topics 101-200.
+	\item The \textbf{robust} 2004 \cite{Voorhees2005} topics, numbering 250, from TREC disks 4 and 5.
+	\item The \textbf{wt10g} collection \cite{Bailey2003} with the 100 topics from the 2000 and 2001 TREC Web tracks.
 \end{itemize}
@@
 
-For each collection, we produce eight runs representing a combination of expansion source and query expansion type.
+For each collection, we produce eight runs representing a combination of expansion source and query expansion model.
+Expansion source refers to the collection(s) used for document expansion, while the query expansion model refers to unexpanded queries (QL) or expanded queries (RM3).
 
@@
 \begin{itemize}
+	\item no expansion, called \textit{baseline};
 	\item the target collection itself, called \textit{self};
-	\item Wikipedia, called \textit{wiki};
-	\item a mixture of the previous two, called \textit{combined}; or
-	\item no expansion, called \textit{baseline};
+	\item Wikipedia, called \textit{wiki}; or
+	\item a mixture of the previous two, called \textit{combined}.
 \end{itemize}
 
-\noindent For each source, both the QL and RM3 variations are tested.
+\noindent For each source, both the QL and RM3 variations are compared.
 
@@
 \begin{table}[htb]
+\caption{Parameter settings for the document expansion procedure and retrieval model}
 \centering
@@
 \end{tabular}
-\caption{Parameter settings for the document expansion procedure and retrieval model}
 \label{table.parameters}
@@
 
-\begin{figure*}
-\centering
-\includegraphics[width=\linewidth]{figures/expansion-sweep.pdf}
-\caption{Sweeps over the number of expansion documents, $n = \{0, 1, 5, 10, 50\}$, for the \textit{self} and \textit{wiki} QL runs.}
-\label{figure.n-sweeps}
-\end{figure*}
-
-\begin{table}
+\begin{table}[!ht]
+\caption{Performance of runs using various expansion sources with (\textit{RM3}) and without (\textit{QL}) query expansion.
+Statistical significance at $p \leq 0.05$ is marked with a variety of symbols; underlining further designates $p \leq 0.01$: $\uparrow$ indicates improvement over the baseline QL run; $\Uparrow$ and $\Downarrow$ indicate improvement and decline respectively with respect to the baseline RM3 run; $^{*}$ indicates improvement over the QL run with the same expansion source; $^{S}$ and $^{W}$ indicate improvement over the \textit{self} and \textit{wiki} sources, respectively, of the same run type.
+Bolded runs are the highest raw score for an evaluation metric in a given collection.}
 \begin{tabular}{|c|c|c|l|l|} \hline
-{\bf Corpus} & {\bf \bigcell{l}{Exp. \\ Source}} & {\bf Run} & {\bf MAP} & {\bf nDCG@20} \\ \hline\hline
+{\bf Corpus} & {\bf \bigcell{l}{Exp. \\ Source}} & {\bf Run} & {\bf MAP} & {\bf nDCG@20} \\ \hline
 
@@
 \rule{0pt}{2.5ex} & \multirow{2}{*}{\it Combined} & {\it QL} & 0.2774$^{\underline{\uparrow W}S}$ & 0.4734$^{\underline{\uparrow SW}}$ \\ \cline{3-5}
-\rule{0pt}{2.5ex} & & {\it RM3} & \textbf{0.3342}$^{\underline{\uparrow *}\Uparrow S}$ & 0.4789$^{\underline{\uparrow}}$ \\ \hline\hline
+\rule{0pt}{2.5ex} & & {\it RM3} & \textbf{0.3342}$^{\underline{\uparrow *}\Uparrow S}$ & 0.4789$^{\underline{\uparrow}}$ \\ \hline
 
@@
 \rule{0pt}{2.5ex} & \multirow{2}{*}{\it Combined} & {\it QL} & 0.2417$^{\underline{\uparrow W}}$ & 0.4156$^{\underline{\uparrow\Uparrow W} S}$ \\ \cline{3-5}
-\rule{0pt}{2.5ex} & & {\it RM3} & 0.2672$^{\underline{\uparrow *S}}$ & \textbf{0.4205}$^{\underline{\uparrow\Uparrow S}}$ \\ \hline\hline
+\rule{0pt}{2.5ex} & & {\it RM3} & 0.2672$^{\underline{\uparrow *S}}$ & \textbf{0.4205}$^{\underline{\uparrow\Uparrow S}}$ \\ \hline
 
@@
 \end{tabular}
-\caption{Performance of runs using various expansion sources with (\textit{RM3}) and without (\textit{QL}) query expansion.
-Statistical significance at $p \leq 0.05$ is marked with a variety of symbols; underlining further designates $p \leq 0.01$: $\uparrow$ indicates improvement over the baseline QL run; $\Uparrow$ and $\Downarrow$ indicate improvement and decline respectively with respect to the baseline RM3 run; $^{*}$ indicates improvement over the QL run with the same expansion source; $^{S}$ and $^{W}$ indicate improvement over the \textit{self} and \textit{wiki} sources, respectively, of the same run type.
-Bolded runs are the highest raw score for an evaluation metric in a given collection.}
 \label{table.effectiveness}
@@
 
+%\afterpage{\clearpage}
+
 \subsection{Sensitivity to \boldmath$n$}\label{section.n-sensitivity}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.76\linewidth]{figures/expansion-sweep.pdf}
+\caption{Sweeps over the number of expansion documents, $n = \{0, 1, 5, 10, 50\}$, for the \textit{self} and \textit{wiki} QL runs.}
+\label{figure.n-sweeps}
+\end{figure*}
 
@@
 We find that we can improve on traditional document expansion by incorporating external collections into the expansion process.
-In the future, we plan to investigate in detail the relationship between homogeneity of documents and the effectiveness of our model.
+In the future, we plan to investigate how important the choice of external collection is to the retrieval effectiveness of our model.
 
